%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
%
% Adapted to be an Rmarkdown template by Mitchell O'Hara-Wild
% 23 November 2018
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%
%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight

\colorlet{awesome}{awesome-red}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\def\endfirstpage{\newpage}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right

\name{Chris}{Oldmeadow}

\position{Director}
\address{Data Sciences, Hunter Medical Research Institute}

\mobile{1410329874}
\email{\href{mailto:christopher.oldmeadow@hmri.org.au}{\nolinkurl{christopher.oldmeadow@hmri.org.au}}}
\homepage{www.chrisoldmeadow.xyz}
\github{ChrisOldmeadow}
\linkedin{chris-oldmeadow}
\twitter{chrisoldmeadow}

% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \skype{skype-id}
% \reddit{reddit-id}


\usepackage{booktabs}

\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%------------------------------------------------------------------------------



% Pandoc CSL macros
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[3] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
% 2019-02-14 Chris Umphlett - add flexibility to the document name in footer, rather than have it be static Curriculum Vitae
\makecvfooter
  {February 2021}
    {Chris Oldmeadow~~~·~~~Curriculum Vitae}
  {\thepage}


%-------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%	Each section is imported separately, open each file in turn to modify content
%------------------------------------------------------------------------------



\hypertarget{biography}{%
\section{Biography}\label{biography}}

Dr Oldmeadow is the Director of the Clinical Research Design, IT and
Statistical Support (CReDITSS) Unit at HMRI. Dr Oldmeadow is an applied
statistician with an international reputation for managing, maintaining
and analysing large complex health related data sets. He oversees
statistical consultancy projects from various fields of research,
including Cancer, Stroke, Cardiology, Respiratory, Public Health, and
Health Services. He has a strong track-record in co-ordinating the
analytic plans of research projects. He has years of experience as the
statistical leader for the design, analysis and data management of
clinical studies, ranging from Pilot/Phase1 through to Phase 4, and
across the spectrum of translational research.

Dr Oldmeadow's methodological expertise spans a broad range of
experimental settings such as single arm trials, parallel group,
cross-over, stepped-wedge; biomarker and diagnostic studies; as well as
observational studies, registries and linked administrative data sets.
He is also actively researching statistical methodologies in
biostatistics in the areas of causal modeling, missing data, and
Bayesian statistics.

\hypertarget{education}{%
\section{Education}\label{education}}

\begin{cventries}
    \cventry{Bachelor of Mathematics (Hon)}{University of Newcastle}{NSW, Australia}{2004}{}\vspace{-4.0mm}
    \cventry{PhD (Statistics)}{Queensland University of Technology}{QLD, Australia}{2009}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{employment-history}{%
\section{Employment History}\label{employment-history}}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
Years & Position & Institute\\
\midrule
\rowcolor{gray!6}  2018-- & Associate Director, Data Sciences & Hunter Medical Research Institute\\
2013--2018 & Senior Statistician & Hunter Medical Research Institute\\
\rowcolor{gray!6}  2009--2013 & Post Doctoral Research Fellow & School of Medicine and Public Health, University of Newcastle\\
2008--2009 & Post Doctoral Research Fellow & Department of Statistics, Monash University\\
\bottomrule
\end{tabular}
\end{table}

\hypertarget{competitive-funding}{%
\section{Competitive funding}\label{competitive-funding}}

Dr Oldmeadow has been awarded over \$14,725,587 in competitive funding
as chief investigator.

\begin{longtable}{r>{\raggedright\arraybackslash}p{15em}>{\raggedright\arraybackslash}p{20em}l}
\toprule
Year & Scheme & Title & Amount\\
\midrule
\rowcolor{gray!6}  2019 & NSW Ministry of Health, Cardiovascular Disease (CVD) Clinician Scientist Grants & Cardioprotective effects of the pneumococcal polysaccharide vaccine & \$600,000.00\\
2019 & NHMRC Target Call Research into Healthy Ageing of Aboriginal and Torres Strait Islander Peoples & Improving implementation of Health Assessments for Aboriginal and Torres Strait Islander clients in mainstream general practice: a cluster randomised controlled trial & \$745,057.00\\
\rowcolor{gray!6}  2019 & NHMRC Project grant & A trial of vaporised nicotine products for smoking cessation following discharge from drug and alcohol residential withdrawal services & \$1,833,513.00\\
2019 & ARC Discovery project & Taking action: Increasing Advance Personal Planning by older adults & \$542,000.00\\
2018 & NHMRC
\rowcolor{gray!6}  Targeted Call for Research - Dementia in Indigenous Australians & Addressing health and care needs of Aboriginal and Torres Strait Islander people living with dementia and their communities & \$3,095,009.00\\
\addlinespace
2018 & Australian Rotary Health & Pilot randomised controlled trial of a telephone delivered intervention for hazardous alcohol use among young people living with severe mental ill-health & \$86,747.00\\
\rowcolor{gray!6}  2018 & NHMRC Global Alliance for Chronic Diseases & 'Indigenous Counselling and Nicotine (ICAN) QUIT in Pregnancy' - a cluster randomised trial to implement culturally competent evidence-based smoking cessation for pregnant Aboriginal and Torres Strait & \$2,318,652.00\\
2018 & NHMRC project grant & Healthy living after stroke: An online intervention for improving stroke survivor health behaviours and quality of life & \$599,124.00\\
\rowcolor{gray!6}  2018 & Dementia and Aged Care Services Research and Innovation Funding Round (DACS) & Does a targeted intervention improve medication safety after discharge and improve outcomes for people with dementia and their carers & \$544,096.00\\
2018 & NHMRC CRE & Aboriginal child  and adolescent health improvement through Aboriginal leadership and collaborative research teams & \$2,499,588.00\\
\addlinespace
\rowcolor{gray!6}  2018 & NSW Ministry of Health AOD Innovation Grants & Routine Outcome Monitoring (ROM) plus feedback in SMART Recovery Australia: A feasibility study examining SMART ROM & \$358,913.00\\
2018 & NSW Ministry of Health AOD Innovation Grants & A randomised controlled trial of a continuing care telephone intervention following residential substance abuse treatment’ & \$517,874.00\\
\rowcolor{gray!6}  2016 & NHMRC Partnership & A randomised controlled trial of the effectiveness of ‘Enable Me’: an e-health innovation for stroke survivors and support persons. & \$253,264.00\\
2016 & National Stroke Foundation & A randomised controlled trial of the effectiveness of ‘Enable Me’: an e-health innovation for stroke survivors and support persons & \$29,444.00\\
\rowcolor{gray!6}  2016 & NSW Ministry of Health & Phase 1 and 2 of the Indigenous Counselling and Nicotine (ICAN) QUIT in Pregnancy & \$136,275.00\\
\addlinespace
2016 & Victorian Responsible Gambling Foundation (TENDER) & The susceptibility, prevalence, type and burden of adolescent gambling: an opportunity for an ongoing monitoring tool & \$174,967.00\\
\rowcolor{gray!6}  2015 & NSW Ministry of Health (TENDER) & Evaluating the Quit for New Life & \$270,908.00\\
2015 & Australian Rotary Health & Improving uptake of colorectal screening among primary care attendees. & \$17,000.00\\
\rowcolor{gray!6}  2015 & Australian Rotary Health & Delivery of care, are we doing enough? An investigation in to the treatment provided for depression in Australian alcohol treatment centers. & \$17,000.00\\
2014 & Hunter Medical Research Institute & Improving uptake of colorectal cancer screening among primary care attendees. & \$37,500.00\\
\addlinespace
\rowcolor{gray!6}  2013 & Cancer Institute NSW & Providing tailored web-based information to support colorectal cancer patients in their preparation for and recovery from surgery: A feasibility study. & \$48,656.00\\
\bottomrule
\end{longtable}

\hypertarget{publications}{%
\section{Publications}\label{publications}}

Dr Oldmeadow has published over 280 journal articles, in peer reviewed
journals including a number in leading journals (e.g.~Nature, Lancet,
Lancet Oncology and Science). He has a H-index of 39 and an i10-index of
118, with 8686 citations since 2009. The topics of his papers reflect
the variety of projects Dr Oldmeadow is involved in.

\hypertarget{bibliography}{}
\leavevmode\hypertarget{ref-bruce_evaluation_2020}{}%
\CSLLeftMargin{1. }
\CSLRightInline{Bruce, R., Murdoch, W., Kable, A., Palazzi, K., Hullick,
C., Pond, D., Oldmeadow, C., Searles, A., Fullerton, A., Fraser, S.,
Ling, R., \& Attia, J. (2020). Evaluation of Carer Strain and Carer
Coping with Medications for People with Dementia after Discharge:
Results from the SMS Dementia Study. \emph{Healthcare (Basel,
Switzerland)}, \emph{8}(3).
\url{https://doi.org/10.3390/healthcare8030248}}

\leavevmode\hypertarget{ref-sutherland_scale-up_2020}{}%
\CSLLeftMargin{2. }
\CSLRightInline{Sutherland, R., Campbell, E., McLaughlin, M., Nathan,
N., Wolfenden, L., Lubans, D. R., Morgan, P. J., Gillham, K., Oldmeadow,
C., Searles, A., Reeves, P., Williams, M., Kajons, N., Bailey, A.,
Boyer, J., Lecathelinais, C., Davies, L., McKenzie, T., Hollis, J., \&
Wiggers, J. (2020). Scale-up of the Physical Activity 4 Everyone (PA4E1)
intervention in secondary schools: 12-month implementation outcomes from
a cluster randomized controlled trial. \emph{The International Journal
of Behavioral Nutrition and Physical Activity}, \emph{17}(1), 100.
\url{https://doi.org/10.1186/s12966-020-01000-y}}

\leavevmode\hypertarget{ref-gunathilake_relationships_2014}{}%
\CSLLeftMargin{3. }
\CSLRightInline{Gunathilake, R., Krishnamurthy, V., Oldmeadow, C., Kerr,
E., Padmakumar, C., Attia, J., Parsons, M., \& Levi, C. (2014).
Relationships between age, other predictive variables, and the 90-day
functional outcome after intravenous thrombolysis for acute ischemic
stroke. \emph{AUSTRALASIAN JOURNAL ON AGEING}, \emph{33}, 19--19.
\url{http://gateway.webofknowledge.com/gateway/Gateway.cgi?GWVersion=2\&SrcApp=PARTNER_APP\&SrcAuth=LinksAMR\&KeyUT=WOS:000337969400027\&DestLinkType=FullRecord\&DestApp=ALL_WOS\&UsrCustomerID=3567906c6fc598e4a73915c2777eae93}}

\leavevmode\hypertarget{ref-sunner_pace-it_2020}{}%
\CSLLeftMargin{4. }
\CSLRightInline{Sunner, C., Giles, M. T., Parker, V., Dilworth, S.,
Bantawa, K., Kable, A., Oldmeadow, C., \& Foureur, M. (2020). PACE-IT
study protocol: A stepped wedge cluster randomised controlled trial
evaluating the implementation of telehealth visual assessment in
emergency care for people living in residential aged-care facilities.
\emph{BMC Health Services Research}, \emph{20}(1), 672.
\url{https://doi.org/10.1186/s12913-020-05539-1}}

\leavevmode\hypertarget{ref-kelly_feasibility_2020}{}%
\CSLLeftMargin{5. }
\CSLRightInline{Kelly, P. J., Beck, A. K., Baker, A. L., Deane, F. P.,
Hides, L., Manning, V., Shakeshaft, A., Larance, B., Neale, J., Kelly,
J., Oldmeadow, C., Searles, A., Treloar, C., Gray, R. M., Argent, A., \&
McGlaughlin, R. (2020). Feasibility of a Mobile Health App for Routine
Outcome Monitoring and Feedback in Mutual Support Groups Coordinated by
SMART Recovery Australia: Protocol for a Pilot Study. \emph{JMIR
Research Protocols}, \emph{9}(7), e15113.
\url{https://doi.org/10.2196/15113}}

\leavevmode\hypertarget{ref-schonberg_development_2020}{}%
\CSLLeftMargin{6. }
\CSLRightInline{Schönberg, S., Asher, R., Stewart, S., Fenwick, M. J.,
Ashton, L., Bucher, T., Van der Horst, K., Oldmeadow, C., Collins, C.
E., \& Shrewsbury, V. A. (2020). Development of the Home Cooking
EnviRonment and Equipment Inventory Observation form (Home-CookERITM):
An Assessment of Content Validity, Face Validity, and Inter-Rater
Agreement. \emph{Nutrients}, \emph{12}(6).
\url{https://doi.org/10.3390/nu12061853}}

\leavevmode\hypertarget{ref-wark_omalizumab_2020}{}%
\CSLLeftMargin{7. }
\CSLRightInline{Wark, P., Hussaini, S., Holder, C., Powell, H., Gibson,
P., \& Oldmeadow, C. (2020). Omalizumab Is an Effective Intervention in
Severe Asthma with Fungal Sensitization. \emph{The Journal of Allergy
and Clinical Immunology. In Practice}.
\url{https://doi.org/10.1016/j.jaip.2020.05.055}}

\leavevmode\hypertarget{ref-allan_stepped_2020}{}%
\CSLLeftMargin{8. }
\CSLRightInline{Allan, J., Nott, S., Chambers, B., Hawthorn, G., Munro,
A., Doran, C., Oldmeadow, C., Coleman, C., \& Saksena, T. (2020). A
stepped wedge trial of efficacy and scalability of a virtual clinical
pharmacy service (VCPS) in rural and remote NSW health facilities.
\emph{BMC Health Services Research}, \emph{20}(1), 373.
\url{https://doi.org/10.1186/s12913-020-05229-y}}

\leavevmode\hypertarget{ref-jones_exploring_2020}{}%
\CSLLeftMargin{9. }
\CSLRightInline{Jones, M., Whitton, C., Tan, A. G., Holliday, E. G.,
Oldmeadow, C., Flood, V. M., Sim, X., Chai, J.-F., Hamzah, H., Klein,
R., Teo, Y.-Y., Mitchell, P., Wong, T. Y., Tai, E. S., Van Dam, R. M.,
Attia, J., \& Wang, J. J. (2020). Exploring Factors Underlying Ethnic
Difference in Age-related Macular Degeneration Prevalence.
\emph{Ophthalmic Epidemiology}, 1--10.
\url{https://doi.org/10.1080/09286586.2020.1762229}}

\leavevmode\hypertarget{ref-clover_which_2016}{}%
\CSLLeftMargin{10. }
\CSLRightInline{Clover, K. A., Oldmeadow, C., Nelson, L., Rogers, K.,
Mitchell, A. J., \& Carter, G. (2016). Which items on the distress
thermometer problem list are the most distressing? \emph{Supportive Care
in Cancer}, \emph{24}(11), 4549--4557.
\url{https://doi.org/10.1007/s00520-016-3294-z}}

\leavevmode\hypertarget{ref-jayakody_unplanned_2018}{}%
\CSLLeftMargin{11. }
\CSLRightInline{Jayakody, A., Oldmeadow, C., Carey, M., Bryant, J.,
Evans, T., Ella, S., Attia, J., \& Sanson-Fisher, R. (2018). Unplanned
readmission or death after discharge for Aboriginal and non-Aboriginal
people with chronic disease in NSW Australia: A retrospective cohort
study. \emph{BMC Health Services Research}, \emph{18}(1).
\url{https://doi.org/10.1186/s12913-018-3723-4}}

\leavevmode\hypertarget{ref-rachakonda_unmet_2015}{}%
\CSLLeftMargin{12. }
\CSLRightInline{Rachakonda, K., George, M., Shafiei, M., \& Oldmeadow,
C. (2015). Unmet Supportive Cancer Care Needs: An Exploratory
Quantitative Study in Rural Australia. \emph{World Journal of Oncology},
\emph{6}(4), 387--393. \url{https://doi.org/10.14740/wjon928w}}

\leavevmode\hypertarget{ref-martin_trog_2019}{}%
\CSLLeftMargin{13. }
\CSLRightInline{Martin, J., Keall, P., Siva, S., Greer, P., Christie,
D., Moore, K., Dowling, J., Pryor, D., Chong, P., McLeod, N., Raman, A.,
Lynam, J., Smart, J., Oldmeadow, C., Tang, C. I., Murphy, D. G., Millar,
J., Tai, K. H., Holloway, L., \ldots{} Sidhom, M. (2019). TROG 18.01
phase III randomised clinical trial of the Novel Integration of New
prostate radiation schedules with adJuvant Androgen deprivation: NINJA
study protocol. \emph{BMJ Open}, \emph{9}(8).
\url{https://doi.org/10.1136/bmjopen-2019-030731}}

\leavevmode\hypertarget{ref-hobden_validity_2017}{}%
\CSLLeftMargin{14. }
\CSLRightInline{Hobden, B., Schwandt, M. L., Carey, M., Lee, M. R.,
Farokhnia, M., Bouhlal, S., Oldmeadow, C., \& Leggio, L. (2017). The
Validity of the Montgomery--Asberg Depression Rating Scale in an
Inpatient Sample with Alcohol Dependence. \emph{Alcoholism: Clinical and
Experimental Research}, \emph{41}(6), 1220--1227.
\url{https://doi.org/10.1111/acer.13400}}

\leavevmode\hypertarget{ref-jackson_role_2018}{}%
\CSLLeftMargin{15. }
\CSLRightInline{Jackson, J. K., Patterson, A. J., MacDonald-Wicks, L.
K., Oldmeadow, C., \& McEvoy, M. A. (2018). The role of inorganic
nitrate and nitrite in cardiovascular disease risk factors: A systematic
review and meta-analysis of human evidence. \emph{Nutrition Reviews},
\emph{76}(5), 348--371. \url{https://doi.org/10.1093/nutrit/nuy005}}

\leavevmode\hypertarget{ref-sutherland_physical_2016}{}%
\CSLLeftMargin{16. }
\CSLRightInline{Sutherland, R. L., Campbell, E. M., Lubans, D. R.,
Morgan, P. J., Nathan, N. K., Wolfenden, L., Okely, A. D., Gillham, K.
E., Hollis, J. L., Oldmeadow, C. J., Williams, A. J., Davies, L. J.,
Wiese, J. S., Bisquera, A., \& Wiggers, J. H. (2016). The Physical
Activity 4 Everyone Cluster Randomized Trial: 2-Year Outcomes of a
School Physical Activity Intervention Among Adolescents. \emph{American
Journal of Preventive Medicine}, \emph{51}(2), 195--205.
\url{https://doi.org/10.1016/j.amepre.2016.02.020}}

\leavevmode\hypertarget{ref-yoshino_interpretation_2012}{}%
\CSLLeftMargin{17. }
\CSLRightInline{Yoshino, O., Quail, A. W., Oldmeadow, C. J., \& Balogh,
Z. J. (2012). The interpretation of intra-abdominal pressures from
animal models: The rabbit to human example. \emph{Injury: International
Journal of the Care of the Injured}, \emph{43}(2), 169--173.}

\leavevmode\hypertarget{ref-bar-zeev_indigenous_2017}{}%
\CSLLeftMargin{18. }
\CSLRightInline{Bar-Zeev, Y., Bonevski, B., Bovill, M., Gruppetta, M.,
Oldmeadow, C., Palazzi, K., Atkins, L., Reath, J., \& Gould, G. S.
(2017). The Indigenous Counselling and Nicotine (ICAN) QUIT in pregnancy
pilot study protocol: A feasibility step-wedge cluster randomised trial
to improve health providers' management of smoking during pregnancy.
\emph{BMJ Open}, \emph{7}(8).
\url{https://doi.org/10.1136/bmjopen-2017-016095}}

\leavevmode\hypertarget{ref-jayakody_impact_2018}{}%
\CSLLeftMargin{19. }
\CSLRightInline{Jayakody, A., Passmore, E., Oldmeadow, C., Bryant, J.,
Carey, M., Simons, E., Cashmore, A., Maher, L., Hennessey, K., Bunfield,
J., Terare, M., Milat, A., \& Sanson-Fisher, R. (2018). The impact of
telephone follow up on adverse events for Aboriginal people with chronic
disease in new South Wales, Australia: A retrospective cohort study.
\emph{International Journal for Equity in Health}, \emph{17}(1).
\url{https://doi.org/10.1186/s12939-018-0776-2}}

\leavevmode\hypertarget{ref-sinclair_ckd-detect_2019}{}%
\CSLLeftMargin{20. }
\CSLRightInline{Sinclair, P. M., Kable, A., Levett-Jones, T., Holder,
C., \& Oldmeadow, C. J. (2019). The CKD-DETECT study: An RCT aimed at
improving intention to initiate a kidney health check in Australian
practice nurses. \emph{Journal of Clinical Nursing}, \emph{28}(15-16),
2745--2759. \url{https://doi.org/10.1111/jocn.14882}}

\leavevmode\hypertarget{ref-dray_systematic_2017}{}%
\CSLLeftMargin{21. }
\CSLRightInline{Dray, J., Bowman, J., Campbell, E., Freund, M.,
Wolfenden, L., Hodder, R. K., McElwaine, K., Tremain, D., Bartlem, K.,
Bailey, J., Small, T., Palazzi, K., Oldmeadow, C., \& Wiggers, J.
(2017). Systematic Review of Universal Resilience-Focused Interventions
Targeting Child and Adolescent Mental Health in the School Setting.
\emph{Journal of the American Academy of Child and Adolescent
Psychiatry}, \emph{56}(10), 813--824.
\url{https://doi.org/10.1016/j.jaac.2017.07.780}}

\leavevmode\hypertarget{ref-dodd_testing_2019}{}%
\CSLLeftMargin{22. }
\CSLRightInline{Dodd, N., Carey, M., Mansfield, E., Oldmeadow, C., \&
Evans, T. (2019). Testing the effectiveness of a general practice
intervention to improve uptake of colorectal cancer screening: A
randomised controlled trial. \emph{Australian and New Zealand Journal of
Public Health}, \emph{43}(5), 464--469.
\url{https://doi.org/10.1111/1753-6405.12913}}

\leavevmode\hypertarget{ref-mccarter_smoking_2018}{}%
\CSLLeftMargin{23. }
\CSLRightInline{McCarter, K., Baker, A., Britton, B., Wolfenden, L.,
Wratten, C., bauer, J., Halpin, S., Carter, G., Beck, A., Leigh, L., \&
Oldmeadow, C. (2018). Smoking, drinking, and depression: Comorbidity in
head and neck cancer patients undergoing radiotherapy. \emph{Cancer
Medicine}, \emph{7}(6), 2382--2390.
\url{https://doi.org/10.1002/cam4.1497}}

\leavevmode\hypertarget{ref-bonevski_smoking_2018}{}%
\CSLLeftMargin{24. }
\CSLRightInline{Bonevski, B., Twyman, L., Paul, C., D'Este, C., West,
R., Siahpush, M., Oldmeadow, C., \& Palazzi, K. (2018). Smoking
cessation intervention delivered by social service organisations for a
diverse population of Australian disadvantaged smokers: A pragmatic
randomised controlled trial. \emph{Preventive Medicine}, \emph{112},
38--44. \url{https://doi.org/10.1016/j.ypmed.2018.04.005}}

\leavevmode\hypertarget{ref-oldmeadow_sifting_2011}{}%
\CSLLeftMargin{25. }
\CSLRightInline{Oldmeadow, C. J., Riveros, R. C., Holliday, E. G.,
Scott, R., Moscato, P. A., Wang, J. J., Mitchell, P., Buitendijk, G. H.
S., Vingerling, J. R., Klaver, C. C. W., Klein, R., \& Attia, J. R.
(2011). Sifting the wheat from the chaff: Prioritizing GWAS results by
identifying consistency across analytical methods. \emph{Genetic
Epidemiology}, \emph{35}(8), 745--754.
\url{https://doi.org/10.1002/gepi.20622}}

\leavevmode\hypertarget{ref-lai_prospective_2017}{}%
\CSLLeftMargin{26. }
\CSLRightInline{Lai, J. S., Hure, A. J., Oldmeadow, C., McEvoy, M.,
Byles, J., \& Attia, J. (2017). Prospective study on the association
between diet quality and depression in mid-aged women over 9~years.
\emph{European Journal of Nutrition}, \emph{56}(1), 273--281.
\url{https://doi.org/10.1007/s00394-015-1078-8}}

\leavevmode\hypertarget{ref-faulkner_prongf_2016}{}%
\CSLLeftMargin{27. }
\CSLRightInline{Faulkner, S., Roselli, S., Demont, Y., Pundavela, J.,
Choquet, G., Leissner, P., Oldmeadow, C., Attia, J., Walker, M. M., \&
Hondermarck, H. (2016). ProNGF is a potential diagnostic biomarker for
thyroid cancer. \emph{Oncotarget}, \emph{7}(19), 28488--28497.
\url{https://doi.org/10.18632/oncotarget.8652}}

\leavevmode\hypertarget{ref-clover_promis_2018}{}%
\CSLLeftMargin{28. }
\CSLRightInline{Clover, K., Lambert, S. D., Oldmeadow, C., Britton, B.,
King, M. T., Mitchell, A. J., \& Carter, G. (2018). PROMIS depression
measures perform similarly to legacy measures relative to a structured
diagnostic interview for depression in cancer patients. \emph{Quality of
Life Research}, \emph{27}(5), 1357--1367.
\url{https://doi.org/10.1007/s11136-018-1803-x}}

\leavevmode\hypertarget{ref-mandaliya_prognostic_2019}{}%
\CSLLeftMargin{29. }
\CSLRightInline{Mandaliya, H., Jones, M., Oldmeadow, C., \& Nordman, I.
I. C. (2019). Prognostic biomarkers in stage IV non-small cell lung
cancer (NSCLC): Neutrophil to lymphocyte ratio (NLR), lymphocyte to
monocyte ratio (LMR), platelet to lymphocyte ratio (PLR) and advanced
lung cancer inflammation index (ALI). \emph{Translational Lung Cancer
Research}, \emph{8}(6), 886--894.
\url{https://doi.org/10.21037/tlcr.2019.11.16}}

\leavevmode\hypertarget{ref-yoong_prevalence_2018}{}%
\CSLLeftMargin{30. }
\CSLRightInline{Yoong, S. L., Stockings, E., Chai, L. K., Tzelepis, F.,
Wiggers, J., Oldmeadow, C., Paul, C., Peruga, A., Kingsland, M., Attia,
J., \& Wolfenden, L. (2018). Prevalence of electronic nicotine delivery
systems (ENDS) use among youth globally: A systematic review and
meta-analysis of country level data. \emph{Australian and New Zealand
Journal of Public Health}, \emph{42}(3), 303--308.
\url{https://doi.org/10.1111/1753-6405.12777}}

\leavevmode\hypertarget{ref-dodd_prevalence_2018}{}%
\CSLLeftMargin{31. }
\CSLRightInline{Dodd, N., Mansfield, E., Carey, M., \& Oldmeadow, C.
(2018). Prevalence of appropriate colorectal cancer screening and
preferences for receiving screening advice among people attending
outpatient clinics. \emph{Australian and New Zealand Journal of Public
Health}, \emph{42}(4), 334--339.
\url{https://doi.org/10.1111/1753-6405.12776}}

\leavevmode\hypertarget{ref-hobden_prevalence_2020}{}%
\CSLLeftMargin{32. }
\CSLRightInline{Hobden, B., Carey, M., Bryant, J., Sanson-Fisher, R., \&
Oldmeadow, C. (2020). Prevalence and Predictors of Symptoms of
Depression Among Individuals Seeking Treatment from Australian Drug and
Alcohol Outpatient Clinics. \emph{Community Mental Health Journal},
\emph{56}(1), 107--115.
\url{https://doi.org/10.1007/s10597-019-00451-3}}

\leavevmode\hypertarget{ref-ho_prescription_2018}{}%
\CSLLeftMargin{33. }
\CSLRightInline{Ho, E., Doherty, M., Thomas, R., Attia, J., Oldmeadow,
C., \& Clapham, M. (2018). Prescription of opioids to post-operative
orthopaedic patients at time of discharge from hospital: A prospective
observational study. \emph{Scandinavian Journal of Pain}, \emph{18}(2),
253--259. \url{https://doi.org/10.1515/sjpain-2017-0149}}

\leavevmode\hypertarget{ref-khan_pre-hospital_2016}{}%
\CSLLeftMargin{34. }
\CSLRightInline{Khan, A. A., Williams, T., Savage, L., Stewart, P.,
Ashraf, A., Davies, A. J., Faddy, S., Attia, J., Oldmeadow, C.,
Bhagwandeen, R., Fletcher, P. J., \& Boyle, A. J. (2016). Pre-hospital
thrombolysis in ST-segment elevation myocardial infarction: A regional
Australian experience. \emph{Medical Journal of Australia},
\emph{205}(3), 121--125. \url{https://doi.org/10.5694/mja15.01336}}

\leavevmode\hypertarget{ref-zdenkowski_patient-reported_2019}{}%
\CSLLeftMargin{35. }
\CSLRightInline{Zdenkowski, N., Butow, P., Spillane, A., Douglas, C.,
Snook, K., Jones, M., Oldmeadow, C., Fewster, S., Beckmore, C., \&
Boyle, F. M. (2019). Patient-reported outcomes with neoadjuvant vs
adjuvant systemic therapy for operable breast cancer. \emph{Breast},
\emph{46}, 25--31. \url{https://doi.org/10.1016/j.breast.2019.04.003}}

\leavevmode\hypertarget{ref-sharmin_parent_2019}{}%
\CSLLeftMargin{36. }
\CSLRightInline{Sharmin, S., Kypri, K., Wadolowski, M., Bruno, R.,
Khanam, M., Aiken, A., Hutchinson, D., Najman, J. M., Slade, T.,
McBride, N., Attia, J., Palazzi, K., Oldmeadow, C., \& Mattick, R. P.
(2019). Parent hazardous drinking and their children's alcohol use in
early and mid-adolescence: Prospective cohort study. \emph{European
Journal of Public Health}, \emph{29}(4), 736--740.
\url{https://doi.org/10.1093/eurpub/ckz029}}

\leavevmode\hypertarget{ref-al-omary_outcomes_2018}{}%
\CSLLeftMargin{37. }
\CSLRightInline{Al-Omary, M. S., Khan, A. A., Davies, A. J., Fletcher,
P. J., Mcivor, D., Bastian, B., Oldmeadow, C., Sverdlov, A. L., Attia,
J. R., \& Boyle, A. J. (2018). Outcomes following heart failure
hospitalization in a regional Australian setting between 2005 and 2014.
\emph{ESC Heart Failure}, \emph{5}(2), 271--278.
\url{https://doi.org/10.1002/ehf2.12239}}

\leavevmode\hypertarget{ref-faulkner_neurotrophin_2018}{}%
\CSLLeftMargin{38. }
\CSLRightInline{Faulkner, S., Jobling, P., Rowe, C. W., Rodrigues
Oliveira, S. M., Roselli, S., Thorne, R. F., Oldmeadow, C., Attia, J.,
Jiang, C. C., Zhang, X. D., Walker, M. M., \& Hondermarck, H. (2018).
Neurotrophin Receptors TrkA, p75NTR, and Sortilin Are Increased and
Targetable in Thyroid Cancer. \emph{American Journal of Pathology},
\emph{188}(1), 229--241.
\url{https://doi.org/10.1016/j.ajpath.2017.09.008}}

\leavevmode\hypertarget{ref-oldmeadow_multiple_2010}{}%
\CSLLeftMargin{39. }
\CSLRightInline{Oldmeadow, C. J., Mengersen, K., Mattick, J. S., \&
Keith, J. M. (2010). Multiple evolutionary rate classes in animal genome
evolution. \emph{Molecular Biology and Evolution}, \emph{27}(4),
942--953. \url{https://doi.org/10.1093/molbev/msp299}}

\leavevmode\hypertarget{ref-wolfenden_multi-strategic_2017}{}%
\CSLLeftMargin{40. }
\CSLRightInline{Wolfenden, L., Nathan, N., Janssen, L. M., Wiggers, J.,
Reilly, K., Delaney, T., Williams, C. M., Bell, C., Wyse, R.,
Sutherland, R., Campbell, L., Lecathelinais, C., Oldmeadow, C., Freund,
M., \& Yoong, S. L. (2017). Multi-strategic intervention to enhance
implementation of healthy canteen policy: A randomised controlled trial.
\emph{Implementation Science}, \emph{12}(1).
\url{https://doi.org/10.1186/s13012-016-0537-9}}

\leavevmode\hypertarget{ref-oldmeadow_model_2011}{}%
\CSLLeftMargin{41. }
\CSLRightInline{Oldmeadow, C. J., \& Keith, J. (2011). Model selection
in Bayesian segmentation of multiple DNA alignments.
\emph{Bioinformatics}, \emph{27}(5), 604--610.
\url{https://doi.org/10.1093/bioinformatics/btq716}}

\leavevmode\hypertarget{ref-seward_measuring_2017}{}%
\CSLLeftMargin{42. }
\CSLRightInline{Seward, K., Wolfenden, L., Wiggers, J., Finch, M., Wyse,
R., Oldmeadow, C., Presseau, J., Clinton-McHarg, T., \& Yoong, S. L.
(2017). Measuring implementation behaviour of menu guidelines in the
childcare setting: Confirmatory factor analysis of a theoretical domains
framework questionnaire (TDFQ). \emph{International Journal of
Behavioral Nutrition and Physical Activity}, \emph{14}(1).
\url{https://doi.org/10.1186/s12966-017-0499-6}}

\leavevmode\hypertarget{ref-morten_managing_2018}{}%
\CSLLeftMargin{43. }
\CSLRightInline{Morten, M., Collison, A., Murphy, V. E., Barker, D.,
Oldmeadow, C., Attia, J., Meredith, J., Powell, H., Robinson, P. D.,
Sly, P. D., Gibson, P. G., \& Mattes, J. (2018). Managing Asthma in
Pregnancy (MAP) trial: FENO levels and childhood asthma. \emph{Journal
of Allergy and Clinical Immunology}, \emph{142}(6), 1765--1772.e4.
\url{https://doi.org/10.1016/j.jaci.2018.02.039}}

\leavevmode\hypertarget{ref-lai_longitudinal_2016}{}%
\CSLLeftMargin{44. }
\CSLRightInline{Lai, J. S., Oldmeadow, C., Hure, A. J., McEvoy, M.,
Byles, J., \& Attia, J. (2016). Longitudinal diet quality is not
associated with depressive symptoms in a cohort of middle-aged
Australian women. \emph{British Journal of Nutrition}, \emph{115}(5),
842--850. \url{https://doi.org/10.1017/S000711451500519X}}

\leavevmode\hypertarget{ref-hoffman_liquor_2017}{}%
\CSLLeftMargin{45. }
\CSLRightInline{Hoffman, G. R., Palazzi, K., Oteng Boateng, B. K., \&
Oldmeadow, C. (2017). Liquor legislation, last drinks, and lockouts: The
Newcastle (Australia) solution. \emph{International Journal of Oral and
Maxillofacial Surgery}, \emph{46}(6), 740--745.
\url{https://doi.org/10.1016/j.ijom.2017.01.019}}

\leavevmode\hypertarget{ref-hure_invited_2016}{}%
\CSLLeftMargin{46. }
\CSLRightInline{Hure, A., Oldmeadow, C., \& Attia, J. (2016). Invited
commentary: Improving estimates of severe acute malnutrition requires
more data. \emph{American Journal of Epidemiology}, \emph{184}(12),
870--872. \url{https://doi.org/10.1093/aje/kww131}}

\leavevmode\hypertarget{ref-oldmeadow_investigation_2008}{}%
\CSLLeftMargin{47. }
\CSLRightInline{Oldmeadow, C. J., Wood, I., Mengersen, K., Visscher, P.
M., Martin, N. G., \& Duffy, D. L. (2008). Investigation of the
relationship between smoking and appendicitis in Australian twins.
\emph{Annals of Epidemiology}, \emph{18}(8), 631--636.
\url{https://doi.org/10.1016/j.annepidem.2008.04.004}}

\leavevmode\hypertarget{ref-chen_influence_2017}{}%
\CSLLeftMargin{48. }
\CSLRightInline{Chen, C., Parsons, M. W., Clapham, M., Oldmeadow, C.,
Levi, C. R., Lin, L., Cheng, X., Lou, M., Kleinig, T. J., Butcher, K.
S., Dong, Q., \& Bivard, A. (2017). Influence of penumbral reperfusion
on clinical outcome depends on baseline ischemic core volume.
\emph{Stroke}, \emph{48}(10), 2739--2745.
\url{https://doi.org/10.1161/STROKEAHA.117.018587}}

\leavevmode\hypertarget{ref-lai_inflammation_2016}{}%
\CSLLeftMargin{49. }
\CSLRightInline{Lai, J. S., Oldmeadow, C., Hure, A. J., McEvoy, M.,
Hiles, S. A., Boyle, M., \& Attia, J. (2016). Inflammation mediates the
association between fatty acid intake and depression in older men and
women. \emph{Nutrition Research}, \emph{36}(3), 234--245.
\url{https://doi.org/10.1016/j.nutres.2015.11.017}}

\leavevmode\hypertarget{ref-carey_improving_2016}{}%
\CSLLeftMargin{50. }
\CSLRightInline{Carey, M., Sanson-Fisher, R., Oldmeadow, C., Mansfield,
E., \& Walsh, J. (2016). Improving self-management of cancer risk
factors, underscreening for cancer and depression among general practice
patients: Study protocol of a randomised controlled trial. \emph{BMJ
Open}, \emph{6}(11). \url{https://doi.org/10.1136/bmjopen-2016-014782}}

\leavevmode\hypertarget{ref-carey_improving_2020}{}%
\CSLLeftMargin{51. }
\CSLRightInline{Carey, M., Sanson-Fisher, R., Zwar, N., Mazza, D.,
Meadows, G., Piterman, L., Waller, A., Walsh, J., Oldmeadow, C.,
Deeming, S., Searles, A., Henskens, F., \& Kelly, B. (2020). Improving
depression outcomes among Australian primary care patients: Protocol for
a cluster randomised controlled trial. \emph{BMJ Open}, \emph{10}(2).
\url{https://doi.org/10.1136/bmjopen-2019-032057}}

\leavevmode\hypertarget{ref-giles_implementation_2019}{}%
\CSLLeftMargin{52. }
\CSLRightInline{Giles, M., Graham, L., Ball, J., King, J., Watts, W.,
Harris, A., Oldmeadow, C., Ling, R., Paul, M., O'Brien, A., Parker, V.,
Wiggers, J., \& Foureur, M. (2019). Implementation of a multifaceted
nurse-led intervention to reduce indwelling urinary catheter use in four
Australian hospitals: A cluster controlled study. \emph{Journal of
Clinical Nursing}, \emph{Print-Electronic}.
\url{https://doi.org/10.1111/jocn.15142}}

\leavevmode\hypertarget{ref-dowse_impact_2020}{}%
\CSLLeftMargin{53. }
\CSLRightInline{Dowse, E., Chan, S., Ebert, L., Wynne, O., Thomas, S.,
Jones, D., Fealy, S., Evans, T.-J., \& Oldmeadow, C. (2020). Impact of
maternal perinatal depression and anxiety on birth outcomes: A
retrospective data analysis. \emph{Maternal and Child Health Journal},
\emph{MACI-D-19-00319}.
\url{https://doi.org/10.1007/s10995-020-02906-6}}

\leavevmode\hypertarget{ref-saluja_impact_2020}{}%
\CSLLeftMargin{54. }
\CSLRightInline{Saluja, T., Davies, A., Oldmeadow, C., \& Boyle, A.
(2020). Impact of Fast food Outlet Density on Incidence of Myocardial
Infarction in the Hunter Region. \emph{Internal Medicine Journal},
\emph{Print-Electronic}. \url{https://doi.org/10.1111/imj.14745}}

\leavevmode\hypertarget{ref-kepreotes_high-flow_2017}{}%
\CSLLeftMargin{55. }
\CSLRightInline{Kepreotes, E., Whitehead, B., Attia, J., Oldmeadow, C.,
Collison, A., Searles, A., Goddard, B., Hilton, J., Lee, M., \& Mattes,
J. (2017). High-flow warm humidified oxygen versus standard low-flow
nasal cannula oxygen for moderate bronchiolitis (HFWHO RCT): An open,
phase 4, randomised controlled trial. \emph{The Lancet},
\emph{389}(10072), 930--939.
\url{https://doi.org/10.1016/S0140-6736(17)30061-2}}

\leavevmode\hypertarget{ref-english_frequent_2018}{}%
\CSLLeftMargin{56. }
\CSLRightInline{English, C., Janssen, H., Crowfoot, G., Bourne, J.,
Callister, R., Dunn, A., Oldmeadow, C., Ong, L. K., Palazzi, K.,
Patterson, A., Spratt, N. J., Walker, F. R., Dunstan, D. W., \&
Bernhardt, J. (2018). Frequent, short bouts of light-intensity exercises
while standing decreases systolic blood pressure: Breaking Up Sitting
Time after Stroke (BUST-Stroke) trial. \emph{International Journal of
Stroke}, \emph{13}(9), 932--940.
\url{https://doi.org/10.1177/1747493018798535}}

\leavevmode\hypertarget{ref-whatnall_feasibility_2019}{}%
\CSLLeftMargin{57. }
\CSLRightInline{Whatnall, M. C., Patterson, A. J., Chiu, S., Oldmeadow,
C., \& Hutchesson, M. J. (2019). Feasibility and preliminary efficacy of
the eating advice to students (EATS) brief web-based nutrition
intervention for young adult university students: A pilot randomized
controlled trial. \emph{Nutrients}, \emph{11}(4).
\url{https://doi.org/10.3390/nu11040905}}

\leavevmode\hypertarget{ref-gould_feasibility_2019}{}%
\CSLLeftMargin{58. }
\CSLRightInline{Gould, G. S., Bovill, M., Pollock, L., Bonevski, B.,
Gruppetta, M., Atkins, L., Carson-Chahhoud, K., Boydell, K. M., Gribbin,
G. R., Oldmeadow, C., Hall, A., ICAN QUIT in Pregnancy Pilot Group, \&
Bar-Zeev, Y. (2019). Feasibility and acceptability of Indigenous
Counselling and Nicotine (ICAN) QUIT in Pregnancy multicomponent
implementation intervention and study design for Australian Indigenous
pregnant women: A pilot cluster randomised step-wedge trial.
\emph{Addictive Behaviors}, \emph{90}(Print-Electronic), 176--190.
\url{https://doi.org/10.1016/j.addbeh.2018.10.036}}

\leavevmode\hypertarget{ref-twyman_factors_2016}{}%
\CSLLeftMargin{59. }
\CSLRightInline{Twyman, L., Bonevski, B., Paul, C., Bryant, J., West,
R., Siahpush, M., D'Este, C., Oldmeadow, C., \& Palazzi, K. (2016).
Factors associated with concurrent tobacco smoking and heavy alcohol
consumption within a socioeconomically disadvantaged Australian sample.
\emph{Substance Use and Misuse}, \emph{51}(4), 459--470.
\url{https://doi.org/10.3109/10826084.2015.1122065}}

\leavevmode\hypertarget{ref-revelas_exceptional_2019}{}%
\CSLLeftMargin{60. }
\CSLRightInline{Revelas, M., Thalamuthu, A., Oldmeadow, C., Evans, T.
J., Armstrong, N. J., Riveros, C., Kwok, J. B., Schofield, P. R.,
Brodaty, H., Scott, R. J., Attia, J. R., Sachdev, P. S., \& Mather, K.
A. (2019). Exceptional longevity and polygenic risk for cardiovascular
health. \emph{Genes}, \emph{10}(3).
\url{https://doi.org/10.3390/genes10030227}}

\leavevmode\hypertarget{ref-hyde_electronic_2019}{}%
\CSLLeftMargin{61. }
\CSLRightInline{Hyde, L. L., Boyes, A. W., Mackenzie, L. J., Leigh, L.,
Oldmeadow, C., Riveros, C., \& Sanson-Fisher, R. (2019). Electronic
Health Literacy Among Magnetic Resonance Imaging and Computed Tomography
Medical Imaging Outpatients: Cluster Analysis. \emph{Journal of Medical
Internet Research}, \emph{21}(8), e13423.
\url{https://doi.org/10.2196/13423}}

\leavevmode\hypertarget{ref-collins_efficacy_2017}{}%
\CSLLeftMargin{62. }
\CSLRightInline{Collins, C. E., Morgan, P. J., Hutchesson, M. J.,
Oldmeadow, C., Barker, D., \& Callister, R. (2017). Efficacy of
Web-Based Weight Loss Maintenance Programs: A Randomized Controlled
Trial Comparing Standard Features Versus the Addition of Enhanced
Personalized Feedback over 12 Months. \emph{Behavioral Sciences (Basel,
Switzerland)}, \emph{7}(4). \url{https://doi.org/10.3390/bs7040076}}

\leavevmode\hypertarget{ref-murawski_efficacy_2019}{}%
\CSLLeftMargin{63. }
\CSLRightInline{Murawski, B., Plotnikoff, R. C., Rayward, A. T.,
Oldmeadow, C., Vandelanotte, C., Brown, W. J., \& Duncan, M. (2019).
Efficacy of an m-health physical activity and sleep health intervention
for adults: A randomized waitlist-controlled trial. \emph{AMERICAN
JOURNAL OF PREVENTIVE MEDICINE}, \emph{57}(4), 503--514.
\url{https://doi.org/10.1016/j.amepre.2019.05.009}}

\leavevmode\hypertarget{ref-bailey_effects_2017}{}%
\CSLLeftMargin{64. }
\CSLRightInline{Bailey, K. A., Baker, A. L., McElduff, P., Jones, M. A.,
Oldmeadow, C., \& Kavanagh, D. J. (2017). Effects of Assault Type on
Cognitive Behaviour Therapy for Coexisting Depression and Alcohol
Misuse. \emph{JOURNAL OF CLINICAL MEDICINE}, \emph{6}(7).
\url{https://doi.org/10.3390/jcm6070072}}

\leavevmode\hypertarget{ref-hollis_effects_2016}{}%
\CSLLeftMargin{65. }
\CSLRightInline{Hollis, J. L., Sutherland, R., Campbell, L., Morgan, P.
J., Lubans, D. R., Nathan, N., Wolfenden, L., Okely, A. D., Davies, L.,
Williams, A., Cohen, K. E., Oldmeadow, C., Gillham, K., \& Wiggers, J.
(2016). Effects of a 'school-based' physical activity intervention on
adiposity in adolescents from economically disadvantaged communities:
Secondary outcomes of the 'Physical Activity 4 Everyone' RCT.
\emph{International Journal of Obesity}, \emph{40}(10), 1486--1493.
\url{https://doi.org/10.1038/ijo.2016.107}}

\leavevmode\hypertarget{ref-mccarter_effectiveness_2018}{}%
\CSLLeftMargin{66. }
\CSLRightInline{McCarter, K. L., Baker, A., Britton, B., Beck, A.,
Carter, G., Bauer, J., Wratten, C., Halpin, S., Holliday, E., Oldmeadow,
C., \& Wolfenden, L. (2018). Effectiveness of clinical practice change
strategies in improving dietitian care for head and neck cancer patients
according to evidence based clinical guidelines: A stepped wedge
randomised controlled trial. \emph{Translational Behavioral Medicine},
\emph{8}, 166--174. \url{https://doi.org/10.1093/tbm/ibx016}}

\leavevmode\hypertarget{ref-vandelanotte_effectiveness_2017}{}%
\CSLLeftMargin{67. }
\CSLRightInline{Vandelanotte, C., Kolt, G. S., Caperchione, C. M.,
Savage, T. N., Rosenkranz, R. R., Maeder, A. J., Van Itallie, A., Tague,
R., Oldmeadow, C., Mummery, W. K., \& Duncan, M. J. (2017).
Effectiveness of a Web 2.0 intervention to increase physical activity in
real-world settings: Randomized ecological trial. \emph{Journal of
Medical Internet Research}, \emph{19}(11).
\url{https://doi.org/10.2196/jmir.8484}}

\leavevmode\hypertarget{ref-hodder_effectiveness_2017}{}%
\CSLLeftMargin{68. }
\CSLRightInline{Hodder, R. K., Freund, M., Bowman, J., Wolfenden, L.,
Campbell, E., Dray, J., Lecathelinais, C., Oldmeadow, C., Attia, J., \&
Wiggers, J. (2017). Effectiveness of a pragmatic school-based universal
resilience intervention in reducing tobacco, alcohol and illicit
substance use in a population of adolescents: Cluster-randomised
controlled trial. \emph{BMJ Open}, \emph{7}(8).
\url{https://doi.org/10.1136/bmjopen-2017-016060}}

\leavevmode\hypertarget{ref-dray_effectiveness_2017}{}%
\CSLLeftMargin{69. }
\CSLRightInline{Dray, J., Bowman, J., Campbell, E., Freund, M., Hodder,
R., Wolfenden, L., Richards, J., Leane, C., Green, S., Lecathelinais,
C., Oldmeadow, C., Attia, J., Gillham, K., \& Wiggers, J. (2017).
Effectiveness of a pragmatic school-based universal intervention
targeting student resilience protective factors in reducing mental
health problems in adolescents. \emph{Journal of Adolescence},
\emph{57}, 74--89.
\url{https://doi.org/10.1016/j.adolescence.2017.03.009}}

\leavevmode\hypertarget{ref-o_brien_effectiveness_2016}{}%
\CSLLeftMargin{70. }
\CSLRightInline{O Brien, K. M., Williams, A., Wiggers, J., Wolfenden,
L., Yoong, S., Campbell, E., Kamper, S. J., McAuley, J., Attia, J.,
Oldmeadow, C., \& Williams, C. M. (2016). Effectiveness of a healthy
lifestyle intervention for low back pain and osteoarthritis of the knee:
Protocol and statistical analysis plan for two randomised controlled
trials. \emph{Brazilian Journal of Physical Therapy}, \emph{20}(5),
477--489. \url{https://doi.org/10.1590/bjpt-rbf.2014.0189}}

\leavevmode\hypertarget{ref-wye_effectiveness_2017}{}%
\CSLLeftMargin{71. }
\CSLRightInline{Wye, P. M., Stockings, E. A., Bowman, J. A., Oldmeadow,
C., \& Wiggers, J. H. (2017). Effectiveness of a clinical practice
change intervention in increasing the provision of nicotine dependence
treatment in inpatient psychiatric facilities: An implementation trial.
\emph{BMC Psychiatry}, \emph{17}(1).
\url{https://doi.org/10.1186/s12888-017-1220-7}}

\leavevmode\hypertarget{ref-dunlop_effectiveness_2017}{}%
\CSLLeftMargin{72. }
\CSLRightInline{Dunlop, A. J., Brown, A. L., Oldmeadow, C., Harris, A.,
Gill, A., Sadler, C., Ribbons, K., Attia, J., Barker, D., Ghijben, P.,
Hinman, J., Jackson, M., Bell, J., \& Lintzeris, N. (2017).
Effectiveness and cost-effectiveness of unsupervised
buprenorphine-naloxone for the treatment of heroin dependence in a
randomized waitlist controlled trial. \emph{Drug and Alcohol
Dependence}, \emph{174}, 181--191.
\url{https://doi.org/10.1016/j.drugalcdep.2017.01.016}}

\leavevmode\hypertarget{ref-guillaumier_effect_2019}{}%
\CSLLeftMargin{73. }
\CSLRightInline{Guillaumier, A., Skelton, E., Shakeshaft, A., Farrell,
M., Tzelepis, F., Walsberger, S., D'Este, C., Paul, C., Dunlop, A.,
Stirling, R., Fowlie, C., Kelly, P., Oldmeadow, C., Palazzi, K., \&
Bonevski, B. (2019). Effect of increasing the delivery of smoking
cessation care in alcohol and other drug treatment centres: A
cluster-randomized controlled trial. \emph{Addiction}.
\url{https://doi.org/10.1111/add.14911}}

\leavevmode\hypertarget{ref-paul_dyadic_2017}{}%
\CSLLeftMargin{74. }
\CSLRightInline{Paul, C., Hall, A., Oldmeadow, C., Lynagh, M., Campbell,
S., Bradstock, K., Williamson, A., Carey, M., \& Sanson-Fisher, R.
(2017). Dyadic interdependence of psychosocial outcomes among
haematological cancer survivors and their support persons.
\emph{Supportive Care in Cancer}, \emph{25}(11), 3339--3346.
\url{https://doi.org/10.1007/s00520-017-3751-3}}

\leavevmode\hypertarget{ref-algama_drosophila_2014}{}%
\CSLLeftMargin{75. }
\CSLRightInline{Algama, M., Oldmeadow, C., Tasker, E., Mengersen, K., \&
Keith, J. M. (2014). Drosophila 3′ UTRs are more complex than
protein-coding sequences. \emph{PLoS ONE}, \emph{9}(5).
\url{https://doi.org/10.1371/journal.pone.0097336}}

\leavevmode\hypertarget{ref-hobden_rates_2017}{}%
\CSLLeftMargin{76. }
\CSLRightInline{Hobden, B., Bryant, J., Sanson-Fisher, R., Oldmeadow,
C., \& Carey, M. (2017). Do rates of depression vary by level of alcohol
misuse in Australian general practice? \emph{Australian Journal of
Primary Health}, \emph{23}(3), 263--267.
\url{https://doi.org/10.1071/PY16076}}

\leavevmode\hypertarget{ref-whatnall_determinants_2019}{}%
\CSLLeftMargin{77. }
\CSLRightInline{Whatnall, M. C., Patterson, A. J., Chiu, S., Oldmeadow,
C., \& Hutchesson, M. J. (2019). Determinants of eating behaviours in
Australian university students: A cross-sectional analysis.
\emph{Nutrition and Dietetics}.
\url{https://doi.org/10.1111/1747-0080.12584}}

\leavevmode\hypertarget{ref-attia_deconfounding_2017}{}%
\CSLLeftMargin{78. }
\CSLRightInline{Attia, J. R., Oldmeadow, C., Holliday, E. G., \& Jones,
M. P. (2017). Deconfounding confounding part 2: Using directed acyclic
graphs (DAGs). \emph{Medical Journal of Australia}, \emph{206}(11),
480--482.e1. \url{https://doi.org/10.5694/mja16.01167}}

\leavevmode\hypertarget{ref-ewald_daily_2017}{}%
\CSLLeftMargin{79. }
\CSLRightInline{Ewald, B. D., Oldmeadow, C., \& Attia, J. R. (2017).
Daily step count and the need for hospital care in subsequent years in a
community-based sample of older australians. \emph{Medical Journal of
Australia}, \emph{206}(3), 126--130.
\url{https://doi.org/10.5694/mja16.00640}}

\leavevmode\hypertarget{ref-troy_cryobiopsy_2019}{}%
\CSLLeftMargin{80. }
\CSLRightInline{Troy, L. K., Grainge, C., Corte, T., Williamson, J. P.,
Vallely, M. P., Cooper, W., Mahar, A. M., Lai, S., Mulyadi, E.,
Torzillo, P. J., Salamonsen, M., Don, G., Myers, J., Raghu, G., Lau, E.
M. T., Arnold, D., Cao, C., Cashmore, A., Cleary, S., \ldots{}
Oldmeadow, C. (2019). Cryobiopsy versus open lung biopsy in the
diagnosis of interstitial lung disease (COLDICE): Protocol of a
multicentre study. \emph{BMJ Open Respiratory Research}, \emph{6}(1).
\url{https://doi.org/10.1136/bmjresp-2019-000443}}

\leavevmode\hypertarget{ref-najib_contemporary_2019}{}%
\CSLLeftMargin{81. }
\CSLRightInline{Najib, N., Magin, P., Lasserson, D., Quain, D., Attia,
J., Oldmeadow, C., Garcia-Esperon, C., \& Levi, C. (2019). Contemporary
prognosis of transient ischemic attack patients: A systematic review and
meta-analysis. \emph{International Journal of Stroke}, \emph{14}(5),
460--467. \url{https://doi.org/10.1177/1747493018823568}}

\leavevmode\hypertarget{ref-pezdirc_consuming_2016}{}%
\CSLLeftMargin{82. }
\CSLRightInline{Pezdirc, K., Hutchesson, M. J., Williams, R. L., Rollo,
M. E., Burrows, T. L., Wood, L. G., Oldmeadow, C., \& Collins, C. E.
(2016). Consuming High-Carotenoid Fruit and Vegetables Influences Skin
Yellowness and Plasma Carotenoids in Young Women: A Single-Blind
Randomized Crossover Trial. \emph{Journal of the Academy of Nutrition
and Dietetics}, \emph{116}(8), 1257--1265.
\url{https://doi.org/10.1016/j.jand.2016.03.012}}

\leavevmode\hypertarget{ref-oldmeadow_concordance_2014}{}%
\CSLLeftMargin{83. }
\CSLRightInline{Oldmeadow, C., Holliday, E. G., McEvoy, M., Scott, R.,
Kwok, J. B. J., Mather, K., Sachdev, P., Schofield, P., \& Attia, J.
(2014). Concordance between direct and imputed APOE genotypes using 1000
genomes data. \emph{Journal of Alzheimer's Disease}, \emph{42}(2),
391--393. \url{https://doi.org/10.3233/JAD-140846}}

\leavevmode\hypertarget{ref-hobden_computer_2017}{}%
\CSLLeftMargin{84. }
\CSLRightInline{Hobden, B., Bryant, J., Carey, M., Sanson-Fisher, R., \&
Oldmeadow, C. (2017). Computer tablet or telephone? A randomised
controlled trial exploring two methods of collecting data from drug and
alcohol outpatients. \emph{Addictive Behaviors}, \emph{71}, 111--117.
\url{https://doi.org/10.1016/j.addbeh.2017.03.009}}

\leavevmode\hypertarget{ref-kable_comparison_2019}{}%
\CSLLeftMargin{85. }
\CSLRightInline{Kable, A., Fullerton, A., Fraser, S., Palazzi, K.,
Hullick, C., Oldmeadow, C., Pond, D., Searles, A., Edmunds, K., \&
Attia, J. (2019). Comparison of Potentially Inappropriate Medications
for People with Dementia at Admission and Discharge during An Unplanned
Admission to Hospital: Results from the SMS Dementia Study dagger.
\emph{HEALTHCARE}, \emph{7}(1).
\url{https://doi.org/10.3390/healthcare7010008}}

\leavevmode\hypertarget{ref-whitcher_comparison_2020}{}%
\CSLLeftMargin{86. }
\CSLRightInline{Whitcher, S., Magnusson, M., Gani, J., Oldmeadow, C., \&
Pockney, P. G. (2020). Comparison of colonic neoplasia detection rates
in patients screened inside and outside the National Bowel Cancer
Screening Program. \emph{Medical Journal of Australia}, \emph{212}(6),
275--276. \url{https://doi.org/10.5694/mja2.50508}}

\leavevmode\hypertarget{ref-bonevski_comparing_2015}{}%
\CSLLeftMargin{87. }
\CSLRightInline{Bonevski, B., Twyman, L., Paul, C., D'Este, C., West,
R., Siahpush, M., Oldmeadow, C., Palazzi, K., Bryant, J., \&
Guillaumier, A. (2015). Comparing socially disadvantaged smokers who
agree and decline to participate in a randomised smoking cessation
trial. \emph{BMJ Open}, \emph{5}(9).
\url{https://doi.org/10.1136/bmjopen-2015-008419}}

\leavevmode\hypertarget{ref-holliday_common_2012}{}%
\CSLLeftMargin{88. }
\CSLRightInline{Holliday, E. G., Maguire, J. M., Evans, T.-J., Koblar,
S. A., Jannes, J., Sturm, J., Hankey, G. J., Baker, R., Golledge, J.,
Parsons, M. W., Malik, R., McEvoy, M. A., Biros, E., Lewis, M. D.,
Lincz, L., Peel, R., Oldmeadow, C. J., Smith, W. T., Moscato, P. A.,
\ldots{} Attia, J. R. (2012). Common variants at 6p21.1 are associated
with large artery atherosclerotic stroke. \emph{Nature Genetics},
\emph{44}(10), 1147--1153.}

\leavevmode\hypertarget{ref-oldmeadow_combined_2014}{}%
\CSLLeftMargin{89. }
\CSLRightInline{Oldmeadow, C., Mossman, D., Evans, T., Holliday, E. G.,
Tooney, P. A., Cairns, M. J., Wu, J., Carr, V., Attia, J. R., \& Scott,
R. J. (2014). Combined analysis of exon splicing and genome wide
polymorphism data predict schizophrenia risk loci. \emph{Journal of
Psychiatric Research}, \emph{52}, 44--49.}

\leavevmode\hypertarget{ref-hobden_co-occurring_2018}{}%
\CSLLeftMargin{90. }
\CSLRightInline{Hobden, B., Bryant, J., Sanson-Fisher, R., Oldmeadow,
C., \& Carey, M. (2018). Co-occurring depression and alcohol misuse is
under-identified in general practice: A cross-sectional study.
\emph{Journal of Health Psychology}, \emph{23}(8), 1085--1095.
\url{https://doi.org/10.1177/1359105316643855}}

\leavevmode\hypertarget{ref-levi_cluster-randomized_2020}{}%
\CSLLeftMargin{91. }
\CSLRightInline{Levi, C. R., Attia, J. A., D'Este, C., Ryan, A. E.,
Henskens, F., Kerr, E., Parsons, M. W., Sanson-Fisher, R. W., Bladin, C.
F., Lindley, R. I., Middleton, S., Paul, C. L., Anderson, C., Ang, T.,
Bivard, A., Cadigan, G., Celestino, S., Coles, T., Corbett, A., \ldots{}
Wolfe, N. (2020). Cluster-Randomized Trial of Thrombolysis
Implementation Support in Metropolitan and Regional Australian Stroke
Centers: Lessons for Individual and Systems Behavior Change.
\emph{Journal of the American Heart Association}, \emph{9}(3).
\url{https://doi.org/10.1161/JAHA.119.012732}}

\leavevmode\hypertarget{ref-wyse_cluster_2019}{}%
\CSLLeftMargin{92. }
\CSLRightInline{Wyse, R., Delaney, T., Gibbins, P., Ball, K., Campbell,
K., Yoong, S. L., Seward, K., Zoetemeyer, R., Rissel, C., Wiggers, J.,
Attia, J., Oldmeadow, C., Sutherland, R., Nathan, N., Reilly, K.,
Reeves, P., \& Wolfenden, L. (2019). Cluster randomised controlled trial
of an online intervention to improve healthy food purchases from primary
school canteens: A study protocol of the 'click \& crunch' trial.
\emph{BMJ Open}, \emph{9}(9).
\url{https://doi.org/10.1136/bmjopen-2019-030538}}

\leavevmode\hypertarget{ref-yoong_cafe_2016}{}%
\CSLLeftMargin{93. }
\CSLRightInline{Yoong, S. L., Nathan, N., Wolfenden, L., Wiggers, J.,
Reilly, K., Oldmeadow, C., Wyse, R., Sutherland, R., Delaney, T.,
Butler, P., Janssen, L., Preece, S., \& Williams, C. M. (2016). CAFÉ: A
multicomponent audit and feedback intervention to improve implementation
of healthy food policy in primary school canteens: A randomised
controlled trial. \emph{International Journal of Behavioral Nutrition
and Physical Activity}, \emph{13}(1).
\url{https://doi.org/10.1186/s12966-016-0453-z}}

\leavevmode\hypertarget{ref-jones_understanding_2017}{}%
\CSLLeftMargin{94. }
\CSLRightInline{Jones, M. P., Beath, A., Oldmeadow, C., \& Attia, J. R.
(2017). Understanding statistical hypothesis tests and power.
\emph{MEDICAL JOURNAL OF AUSTRALIA}, \emph{207}(4), 148--150.
\url{https://doi.org/10.5694/mja16.01022}}

\leavevmode\hypertarget{ref-warren_genome-wide_2017}{}%
\CSLLeftMargin{95. }
\CSLRightInline{Warren, H. R., Evangelou, E., Cabrera, C. P., Gao, H.,
Ren, M., Mifsud, B., Ntalla, I., Surendran, P., Liu, C., Cook, J. P.,
Kraja, A. T., Drenos, F., Loh, M., Verweij, N., Marten, J., Karaman, I.,
Lepe, M. P. S., O'Reilly, P. F., Knight, J., \ldots{} Elliott, P.
(2017). Genome-wide association analysis identifies novel blood pressure
loci and offers biological insights into cardiovascular risk (vol 49, pg
403, 2017). \emph{NATURE GENETICS}, \emph{49}(10), 1558--1558.
\url{https://doi.org/10.1038/ng1017-1558a}}

\leavevmode\hypertarget{ref-hobden_clinician_2017}{}%
\CSLLeftMargin{96. }
\CSLRightInline{Hobden, B., Carey, M., Bryant, J., Sanson-Fisher, R., \&
Oldmeadow, C. (2017). Clinician identification of elevated symptoms of
depression among individuals seeking treatment for substance misuse.
\emph{Drug and Alcohol Dependence}, \emph{181}, 71--76.
\url{https://doi.org/10.1016/j.drugalcdep.2017.09.013}}

\leavevmode\hypertarget{ref-regan_comparison_2017}{}%
\CSLLeftMargin{97. }
\CSLRightInline{Regan, T., Paul, C., Ishiguchi, P., D Este, C., Koller,
C., Forshaw, K., Noble, N., Oldmeadow, C., Bisquera, A., \& Eades, S.
(2017). Comparison of two sources of clinical audit data to assess the
delivery of diabetes care in aboriginal communities. \emph{International
Journal of Environmental Research and Public Health}, \emph{14}(10).
\url{https://doi.org/10.3390/ijerph14101236}}

\leavevmode\hypertarget{ref-schumacher_reference_2017}{}%
\CSLLeftMargin{98. }
\CSLRightInline{Schumacher, T. L., Oldmeadow, C., Clausen, D.,
Weatherall, L., Keogh, L., Pringle, K. G., \& Rae, K. M. (2017).
Reference Intervals for Non-Fasting CVD Lipids and Inflammation Markers
in Pregnant Indigenous Australian Women. \emph{Healthcare}, \emph{5}(4),
1--11. \url{https://doi.org/10.3390/healthcare5040072}}

\leavevmode\hypertarget{ref-fletcher_supporting_2017}{}%
\CSLLeftMargin{99. }
\CSLRightInline{Fletcher, R., Kay-Lambkin, F., May, C., Oldmeadow, C.,
Attia, J., \& Leigh, L. (2017). Supporting men through their transition
to fatherhood with messages delivered to their smartphones: A
feasibility study of SMS4dads. \emph{BMC Public Health}, \emph{17}(1).
\url{https://doi.org/10.1186/s12889-017-4978-0}}

\leavevmode\hypertarget{ref-gould_clinicians_2017}{}%
\CSLLeftMargin{100. }
\CSLRightInline{Gould, G. S., Zeev, Y. B., Tywman, L., Oldmeadow, C.,
Chiu, S., Clarke, M., \& Bonevski, B. (2017). Do Clinicians Ask Pregnant
Women about Exposures to Tobacco and Cannabis Smoking, Second-Hand-Smoke
and E-Cigarettes? An Australian National Cross-Sectional Survey.
\emph{International Journal of Environmental Research and Public
Health}, \emph{14}(12). \url{https://doi.org/10.3390/ijerph14121585}}

\leavevmode\hypertarget{ref-whiting_general_2017}{}%
\CSLLeftMargin{101. }
\CSLRightInline{Whiting, G., Magin, P., Morgan, S., Tapley, A.,
Henderson, K., Oldmeadow, C., Ball, J., Driel, M. van, Spike, N.,
McArthur, L., Scott, J., \& Stocks, N. (2017). General practice
trainees' clinical experience of dermatology indicates a need for
improved education: A cross-sectional analysis from the Registrar
Clinical Encounters in Training Study. \emph{Australasian Journal of
Dermatology}, \emph{58}(4), e199--e206.
\url{https://doi.org/10.1111/ajd.12493}}

\leavevmode\hypertarget{ref-holmes_cd36_2018}{}%
\CSLLeftMargin{102. }
\CSLRightInline{Holmes, M., Connor, T., Oldmeadow, C., Pockney, P. G.,
Scott, R. J., \& Talseth-Palmer, B. A. (2018). CD36 - a plausible
modifier of disease phenotype in familial adenomatous polyposis.
\emph{Hereditary Cancer in Clinical Practice}, \emph{16}(1).
\url{https://doi.org/10.1186/s13053-018-0096-y}}

\leavevmode\hypertarget{ref-holliday_pattern_2017}{}%
\CSLLeftMargin{103. }
\CSLRightInline{Holliday, S. M., Morgan, S., Tapley, A., Henderson, K.
M., Dunlop, A. J., Driel, M. L. van, Spike, N. A., McArthur, L. A.,
Ball, J., Oldmeadow, C. J., \& Magin, P. J. (2017). The pattern of
anxiolytic and hypnotic management by Australian general practice
trainees. \emph{Drug and Alcohol Review}, \emph{36}(2), 261--269.
\url{https://doi.org/10.1111/dar.12404}}

\leavevmode\hypertarget{ref-kolt_using_2017}{}%
\CSLLeftMargin{104. }
\CSLRightInline{Kolt, G. S., Rosenkranz, R. R., Vandelanotte, C.,
Caperchione, C. M., Maeder, A. J., Tague, R., Savage, T. N., Van
Itallie, A., Mummery, W. K., Oldmeadow, C., \& Duncan, M. J. (2017).
Using web 2.0 applications to promote health-related physical activity:
Findings from the WALK 2.0 randomised controlled trial. \emph{British
Journal of Sports Medicine}, \emph{51}(19), 1433--1440.
\url{https://doi.org/10.1136/bjsports-2016-096890}}

\leavevmode\hypertarget{ref-james_correlates_2018}{}%
\CSLLeftMargin{105. }
\CSLRightInline{James, C., James, C., Calear, A. L., Tynan, R., Roach,
D., Leigh, L., Oldmeadow, C., Rahman, M., \& Kelly, B. (2018).
Correlates of psychological distress among workers in the mining
industry in remote Australia: Evidence from a multi-site cross-sectional
survey. \emph{PLOS ONE}, \emph{13}(12).
\url{https://doi.org/10.1371/journal.pone.0209377}}

\leavevmode\hypertarget{ref-lee_gene_2018}{}%
\CSLLeftMargin{106. }
\CSLRightInline{Lee, J. J., Wedow, R., Okbay, A., Kong, E., Maghzian,
O., Zacher, M., Nguyen-Viet, T. A., Bowers, P., Sidorenko, J., Karlsson
Linnér, R., Fontana, M. A., Kundu, T., Lee, C., Li, H., Li, R., Royer,
R., Timshel, P. N., Walters, R. K., Willoughby, E. A., \ldots{} Poot, R.
A. (2018). Gene discovery and polygenic prediction from a genome-wide
association study of educational attainment in 1.1 million individuals.
\emph{Nature Genetics}, \emph{50}(8), 1112--1121.
\url{https://doi.org/10.1038/s41588-018-0147-3}}

\leavevmode\hypertarget{ref-ren_pneumococcal_2018}{}%
\CSLLeftMargin{107. }
\CSLRightInline{Ren, S., Holliday, E., Hure, A., Peel, R., Hancock, S.,
Leigh, L., Oldmeadow, C., Newby, D., Li, S. C., \& Attia, J. (2018).
Pneumococcal polysaccharide vaccine associated with reduced lengths of
stay for cardiovascular events hospital admissions: Experience from the
Hunter Community Study. \emph{Vaccine}, \emph{36}(49), 7520--7524.
\url{https://doi.org/10.1016/j.vaccine.2018.10.064}}

\leavevmode\hypertarget{ref-sanson-fisher_simple_2018}{}%
\CSLLeftMargin{108. }
\CSLRightInline{Sanson-Fisher, R. W., Noble, N. E., Searles, A. M.,
Deeming, S., Smits, R. E., Oldmeadow, C. J., \& Bryant, J. (2018). A
simple filter model to guide the allocation of healthcare resources for
improving the treatment of depression among cancer patients. \emph{BMC
Cancer}, \emph{18}(1). \url{https://doi.org/10.1186/s12885-018-4009-2}}

\leavevmode\hypertarget{ref-fradgley_system-wide_2018}{}%
\CSLLeftMargin{109. }
\CSLRightInline{Fradgley, E. A., Paul, C. L., Bryant, J., Zucca, A., \&
Oldmeadow, C. (2018). System-wide and group-specific health service
improvements: Cross-sectional survey of outpatient improvement
preferences and associations with demographic characteristics.
\emph{International Journal of Environmental Research and Public
Health}, \emph{15}(2). \url{https://doi.org/10.3390/ijerph15020179}}

\leavevmode\hypertarget{ref-zdenkowski_single-arm_2018}{}%
\CSLLeftMargin{110. }
\CSLRightInline{Zdenkowski, N., Butow, P., Spillane, A., Douglas, C.,
Snook, K., Jones, M., Oldmeadow, C., Fewster, S., Beckmore, C., \&
Boyle, F. M. (2018). Single-arm longitudinal study to evaluate a
decision aid for women offered Neoadjuvant systemic therapy for operable
breast cancer. \emph{JNCCN Journal of the National Comprehensive Cancer
Network}, \emph{16}(4), 378--385.
\url{https://doi.org/10.6004/jnccn.2017.7063}}

\leavevmode\hypertarget{ref-joshi_glycaemic_2018}{}%
\CSLLeftMargin{111. }
\CSLRightInline{Joshi, T., Pullen, S.-J., Gebuehr, A., Oldmeadow, C.,
Attia, J. R., \& Acharya, S. H. (2018). Glycaemic optimization for
patients with cardiac disease-A before-and-after study.
\emph{International Journal of Clinical Practice},
\emph{72}(Print-Electronic), e13086--e13086.
\url{https://doi.org/10.1111/ijcp.13086}}

\leavevmode\hypertarget{ref-davies_study_2018}{}%
\CSLLeftMargin{112. }
\CSLRightInline{Davies, G., Lam, M., Harris, S. E., Trampush, J. W.,
Luciano, M., Hill, W. D., Hagenaars, S. P., Ritchie, S. J., Marioni, R.
E., Fawns-Ritchie, C., Liewald, D. C. M., Okely, J. A., Ahola-Olli, A.
V., Barnes, C. L. K., Bertram, L., Bis, J. C., Burdick, K. E.,
Christoforou, A., Derosse, P., \ldots{} Kleineidam, L. (2018). Study of
300,486 individuals identifies 148 independent genetic loci influencing
general cognitive function. \emph{Nature Communications}, \emph{9}(1).
\url{https://doi.org/10.1038/s41467-018-04362-x}}

\leavevmode\hypertarget{ref-barnett_survival_2018}{}%
\CSLLeftMargin{113. }
\CSLRightInline{Barnett, A. G., Oldmeadow, C., \& Attia, J. R. (2018).
Survival studies: Competing risks, immortality and censoring.
\emph{Medical Journal of Australia}, \emph{208}(11).
\url{https://doi.org/10.5694/mja17.00171}}

\leavevmode\hypertarget{ref-hodder_differential_2018}{}%
\CSLLeftMargin{114. }
\CSLRightInline{Hodder, R. K., Freund, M., Bowman, J., Wolfenden, L.,
Campbell, E., Dray, J., Lecathelinais, C., Oldmeadow, C., Attia, J., \&
Wiggers, J. (2018). Differential intervention effectiveness of a
universal school-based resilience intervention in reducing adolescent
substance use within student subgroups: Exploratory assessment within a
cluster-randomised controlled trial. \emph{BMJ Open}, \emph{8}(8).
\url{https://doi.org/10.1136/bmjopen-2017-021047}}

\leavevmode\hypertarget{ref-dodd_have_2018}{}%
\CSLLeftMargin{115. }
\CSLRightInline{Dodd, N., Mansfield, E., Carey, M., Oldmeadow, C., \&
Sanson-Fisher, R. (2018). Have we increased our efforts to identify
strategies which encourage colorectal cancer screening in primary care
patients? A review of research outputs over time. \emph{Preventive
Medicine Reports}, \emph{11}, 100--104.
\url{https://doi.org/10.1016/j.pmedr.2018.05.015}}

\leavevmode\hypertarget{ref-evangelou_genetic_2018}{}%
\CSLLeftMargin{116. }
\CSLRightInline{Evangelou, E., Warren, H. R., Mosen-Ansorena, D.,
Mifsud, B., Pazoki, R., Gao, H., Ntritsos, G., Dimou, N., Cabrera, C.
P., Karaman, I., Ng, F. L., Evangelou, M., Witkowska, K., Tzanis, E.,
Hellwege, J. N., Giri, A., Velez Edwards, D. R., Sun, Y. V., Cho, K.,
\ldots{} Gandin, I. (2018). Genetic analysis of over 1 million people
identifies 535 new loci associated with blood pressure traits.
\emph{Nature Genetics}, \emph{50}(10), 1412--1425.
\url{https://doi.org/10.1038/s41588-018-0205-x}}

\leavevmode\hypertarget{ref-ligthart_genome_2018}{}%
\CSLLeftMargin{117. }
\CSLRightInline{Ligthart, S., Vaez, A., Võsa, U., Stathopoulou, M. G.,
Vries, P. S. de, Prins, B. P., Van der Most, P. J., Tanaka, T., Naderi,
E., Rose, L. M., Wu, Y., Karlsson, R., Barbalic, M., Lin, H., Pool, R.,
Zhu, G., Macé, A., Sidore, C., Trompet, S., \ldots{} Morris, A. P.
(2018). Genome Analyses of \textgreater200,000 Individuals Identify 58
Loci for Chronic Inflammation and Highlight Pathways that Link
Inflammation and Complex Disorders. \emph{American Journal of Human
Genetics}, \emph{103}(5), 691--706.
\url{https://doi.org/10.1016/j.ajhg.2018.09.009}}

\leavevmode\hypertarget{ref-abdullah_differing_2018}{}%
\CSLLeftMargin{118. }
\CSLRightInline{Abdullah, N., Murad, N. A. A., Attia, J., Oldmeadow, C.,
Kamaruddin, M. A., Jalal, N. A., Ismail, N., Jamal, R., Scott, R. J., \&
Holliday, E. G. (2018). Differing contributions of classical risk
factors to type 2 diabetes in multi-ethnic Malaysian populations.
\emph{International Journal of Environmental Research and Public
Health}, \emph{15}(12). \url{https://doi.org/10.3390/ijerph15122813}}

\leavevmode\hypertarget{ref-wyss_multiethnic_2018}{}%
\CSLLeftMargin{119. }
\CSLRightInline{Wyss, A. B., Sofer, T., Lee, M. K., Terzikhan, N.,
Nguyen, J. N., Lahousse, L., Latourelle, J. C., Smith, A. V., Bartz, T.
M., Feitosa, M. F., Gao, W., Ahluwalia, T. S., Tang, W., Oldmeadow, C.,
Duan, Q., Jong, K. de, Wojczynski, M. K., Wang, X. Q., Noordam, R.,
\ldots{} Psaty, B. M. (2018). Multiethnic meta-analysis identifies
ancestry-specific and cross-ancestry loci for pulmonary function.
\emph{Nature Communications}, \emph{9}(1).
\url{https://doi.org/10.1038/s41467-018-05369-0}}

\leavevmode\hypertarget{ref-thibault_prolonged_2018}{}%
\CSLLeftMargin{120. }
\CSLRightInline{Thibault, P., Attia, J., \& Oldmeadow, C. (2018). A
prolonged antibiotic protocol to treat persistent Chlamydophila
pneumoniae infection improves the extracranial venous circulation in
multiple sclerosis. \emph{Phlebology}, \emph{33}(6), 397--406.
\url{https://doi.org/10.1177/0268355517712884}}

\leavevmode\hypertarget{ref-sharma_first_2018}{}%
\CSLLeftMargin{121. }
\CSLRightInline{Sharma, B. B., Loxton, D. J., Murray, H., Angeli, G. L.,
Oldmeadow, C., Chiu, S., \& Smith, R. (2018). A first step to improving
maternal mortality in a low-literacy setting; the successful use of
singing to improve knowledge regarding antenatal care. \emph{American
Journal of Obstetrics and Gynecology}, \emph{219}(6), 615.e1--615.e11.
\url{https://doi.org/10.1016/j.ajog.2018.09.038}}

\leavevmode\hypertarget{ref-bar-zeev_clinician_2018}{}%
\CSLLeftMargin{122. }
\CSLRightInline{Bar-Zeev, Y., Bonevski, B., Gruppetta, M., Twyman, L.,
Atkins, L., Palazzi, K., Oldmeadow, C., \& Gould, G. S. (2018).
Clinician factors associated with prescribing nicotine replacement
therapy in pregnancy: A cross-sectional survey of Australian
obstetricians and general practitioners. \emph{Australian and New
Zealand Journal of Obstetrics and Gynaecology}, \emph{58}(3), 366--370.
\url{https://doi.org/10.1111/ajo.12751}}

\leavevmode\hypertarget{ref-evangelou_erratum_2018}{}%
\CSLLeftMargin{123. }
\CSLRightInline{Evangelou, E., Warren, H. R., Mosen-Ansorena, D.,
Mifsud, B., Pazoki, R., Gao, H., Ntritsos, G., Dimou, N., Cabrera, C.
P., Karaman, I., Ng, F. L., Evangelou, M., Witkowska, K., Tzanis, E.,
Hellwege, J. N., Giri, A., Velez Edwards, D. R., Sun, Y. V., Cho, K.,
\ldots{} Gandin, I. (2018). Erratum to: Genetic analysis of over 1
million people identifies 535 new loci associated with blood pressure
traits (Nature Genetics, (2018), 50, 10, (1412-1425),
10.1038/s41588-018-0205-x). \emph{Nature Genetics}, \emph{50}(12), 1755.
\url{https://doi.org/10.1038/s41588-018-0297-3}}

\leavevmode\hypertarget{ref-carey_examining_2018}{}%
\CSLLeftMargin{124. }
\CSLRightInline{Carey, M., Sanson-Fisher, R., Clinton-McHarg, T., Boyes,
A., Olver, I., Oldmeadow, C., Paul, C., D'Este, C., \& Henskens, F.
(2018). Examining variation across treatment clinics in cancer patients'
psychological outcomes: Results of a cross sectional survey.
\emph{Supportive Care in Cancer}, \emph{26}(9), 3201--3208.
\url{https://doi.org/10.1007/s00520-018-4188-z}}

\leavevmode\hypertarget{ref-hobden_finding_2018}{}%
\CSLLeftMargin{125. }
\CSLRightInline{Hobden, B., Bryant, J., Carey, M., Baker, A. L.,
Farrell, M., Oldmeadow, C., Mattick, R. P., Shakeshaft, A., \&
Sanson-Fisher, R. (2018). Finding the optimal treatment model: A
systematic review of treatment for co-occurring alcohol misuse and
depression. \emph{Australian and New Zealand Journal of Psychiatry},
\emph{52}(8), 737--750. \url{https://doi.org/10.1177/0004867418758922}}

\leavevmode\hypertarget{ref-bryant_how_2018}{}%
\CSLLeftMargin{126. }
\CSLRightInline{Bryant, J., Hobden, B., Forshaw, K., Oldmeadow, C.,
Walsh, J., \& Sanson-Fisher, R. (2018). How accurately do general
practitioners detect concurrent tobacco use and risky alcohol
consumption? A cross-sectional study in Australian general practice.
\emph{Australian Journal of Primary Health}, \emph{24}(5), 378--384.
\url{https://doi.org/10.1071/PY17122}}

\leavevmode\hypertarget{ref-revelas_review_2018}{}%
\CSLLeftMargin{127. }
\CSLRightInline{Revelas, M., Thalamuthu, A., Oldmeadow, C., Evans, T.
J., Armstrong, N. J., Kwok, J. B., Brodaty, H., Schofield, P. R., Scott,
R. J., Sachdev, P. S., Attia, J. R., \& Mather, K. A. (2018). Review and
meta-analysis of genetic polymorphisms associated with exceptional human
longevity. \emph{Mechanisms of Ageing and Development}, \emph{175},
24--34. \url{https://doi.org/10.1016/j.mad.2018.06.002}}

\leavevmode\hypertarget{ref-twyman_what_2018}{}%
\CSLLeftMargin{128. }
\CSLRightInline{Twyman, L., Bonevski, B., Paul, C., Bryant, J., West,
R., Siahpush, M., D'este, C., Oldmeadow, C., \& Palazzi, K. (2018). What
factors are associated with abstinence amongst socioeconomically
disadvantaged smokers? A cross-sectional survey of use of cessation aids
and quitting approach. \emph{Drug and Alcohol Review}, \emph{37}(2),
170--179. \url{https://doi.org/10.1111/dar.12561}}

\leavevmode\hypertarget{ref-twyman_theyre_2019}{}%
\CSLLeftMargin{129. }
\CSLRightInline{Twyman, L., Cowles, C., Walsberger, S. C., Baker, A. L.,
\& Bonevski, B. (2019). {``They're going to smoke anyway''}: A
qualitative study of community mental health staff and consumer
perspectives on the role of social and living environments in tobacco
use and cessation. \emph{Frontiers in Psychiatry}, \emph{10}(JUN),
1--11. \url{https://doi.org/10.3389/fpsyt.2019.00503}}

\leavevmode\hypertarget{ref-smith_case_2019}{}%
\CSLLeftMargin{130. }
\CSLRightInline{Smith, R., Mohapatra, L., Hunter, M., Evans, T. J.,
Oldmeadow, C., Holliday, E., Hure, A., \& Attia, J. (2019). A case for
not adjusting birthweight customized standards for ethnicity:
Observations from a unique Australian cohort. \emph{American Journal of
Obstetrics and Gynecology}, \emph{220}(3), 277.e1--277.e10.
\url{https://doi.org/10.1016/j.ajog.2018.10.094}}

\leavevmode\hypertarget{ref-karlsson_linner_genome-wide_2019}{}%
\CSLLeftMargin{131. }
\CSLRightInline{Karlsson Linnér, R., Biroli, P., Kong, E., Meddens, S.
F. W., Wedow, R., Fontana, M. A., Lebreton, M., Tino, S. P., Abdellaoui,
A., Hammerschlag, A. R., Nivard, M. G., Okbay, A., Rietveld, C. A.,
Timshel, P. N., Trzaskowski, M., Vlaming, R. D., Zünd, C. L., Bao, Y.,
Buzdugan, L., \ldots{} Perola, M. (2019). Genome-wide association
analyses of risk tolerance and risky behaviors in over 1 million
individuals identify hundreds of loci and shared genetic influences.
\emph{Nature Genetics}, \emph{51}(2), 245--257.
\url{https://doi.org/10.1038/s41588-018-0309-3}}

\leavevmode\hypertarget{ref-denham_short-term_2019}{}%
\CSLLeftMargin{132. }
\CSLRightInline{Denham, J. W., Joseph, D., Lamb, D. S., Spry, N. A.,
Duchesne, G., Matthews, J., Atkinson, C., Tai, K. H., Christie, D.,
Kenny, L., Turner, S., Gogna, N. K., Diamond, T., Delahunt, B.,
Oldmeadow, C., Attia, J., \& Steigler, A. (2019). Short-term androgen
suppression and radiotherapy versus intermediate-term androgen
suppression and radiotherapy, with or without zoledronic acid, in men
with locally advanced prostate cancer (TROG 03.04 RADAR): 10-year
results from a randomised, phase 3, factorial trial. \emph{The Lancet
Oncology}, \emph{20}(2), 267--281.
\url{https://doi.org/10.1016/S1470-2045(18)30757-5}}

\leavevmode\hypertarget{ref-morten_intron_2019}{}%
\CSLLeftMargin{133. }
\CSLRightInline{Morten, B. C., Chiu, S., Oldmeadow, C., Lubinski, J.,
Scott, R. J., \& Avery-Kiejda, K. A. (2019). The intron 3 16~bp
duplication polymorphism of p53 (rs17878362) is not associated with
increased risk of developing triple-negative breast cancer. \emph{Breast
Cancer Research and Treatment}, \emph{173}(3), 727--733.
\url{https://doi.org/10.1007/s10549-018-5039-9}}

\leavevmode\hypertarget{ref-jamaluddin_proteomic_2019}{}%
\CSLLeftMargin{134. }
\CSLRightInline{Jamaluddin, M. F. B., Nagendra, P. B., Nahar, P.,
Oldmeadow, C., \& Tanwar, P. S. (2019). Proteomic Analysis Identifies
Tenascin-C Expression Is Upregulated in Uterine Fibroids.
\emph{Reproductive Sciences}, \emph{26}(4), 476--486.
\url{https://doi.org/10.1177/1933719118773420}}

\leavevmode\hypertarget{ref-giri_trans-ethnic_2019}{}%
\CSLLeftMargin{135. }
\CSLRightInline{Giri, A., Hellwege, J. N., Keaton, J. M., Park, J., Qiu,
C., Warren, H. R., Torstenson, E. S., Kovesdy, C. P., Sun, Y. V.,
Wilson, O. D., Robinson-Cohen, C., Roumie, C. L., Chung, C. P.,
Birdwell, K. A., Damrauer, S. M., DuVall, S. L., Klarin, D., Cho, K.,
Wang, Y., \ldots{} Edwards, T. L. (2019). Trans-ethnic association study
of blood pressure determinants in over 750,000 individuals. \emph{Nature
Genetics}, \emph{51}(1), 51--62.
\url{https://doi.org/10.1038/s41588-018-0303-9}}

\leavevmode\hypertarget{ref-jackson_vegetable_2019}{}%
\CSLLeftMargin{136. }
\CSLRightInline{Jackson, J. K., Patterson, A. J., Macdonald-Wicks, L.
K., Forder, P. M., Blekkenhorst, L. C., Bondonno, C. P., Hodgson, J. M.,
Ward, N. C., Holder, C., Oldmeadow, C., Byles, J. E., \& McEvoy, M. A.
(2019). Vegetable nitrate intakes are associated with reduced
self-reported cardiovascular-related complications within a
representative sample of middle-aged australian women, prospectively
followed up for 15 years. \emph{Nutrients}, \emph{11}(2).
\url{https://doi.org/10.3390/nu11020240}}

\leavevmode\hypertarget{ref-britton_reply_2019}{}%
\CSLLeftMargin{137. }
\CSLRightInline{Britton, B., Baker, A. L., Wolfenden, L., Wratten, C.,
Bauer, J., Beck, A. K., McCarter, K., Harrowfield, J., Isenring, E.,
Tang, C., Oldmeadow, C., \& Carter, G. (2019). In Reply to Lee and
Douthit, and Champ and Klement. \emph{International Journal of Radiation
Oncology Biology Physics}, \emph{103}(5), 1283--1284.
\url{https://doi.org/10.1016/j.ijrobp.2018.12.017}}

\leavevmode\hypertarget{ref-eliezer_alpha_2019}{}%
\CSLLeftMargin{138. }
\CSLRightInline{Eliezer, D., Deshpande, A. V., Starkey, M. R., Samnakay,
N., Oldmeadow, C., \& Kernohan, A. (2019). Alpha blockers for treating
functional daytime urinary incontinence in children (Protocol).
\emph{Cochrane Database of Systematic Reviews}, \emph{2019}(4).
\url{https://doi.org/10.1002/14651858.CD013313}}

\leavevmode\hypertarget{ref-davies_author_2019}{}%
\CSLLeftMargin{139. }
\CSLRightInline{Davies, G., Lam, M., Harris, S. E., Trampush, J. W.,
Luciano, M., Hill, W. D., Hagenaars, S. P., Ritchie, S. J., Marioni, R.
E., Fawns-Ritchie, C., Liewald, D. C. M., Okely, J. A., Ahola-Olli, A.
V., Barnes, C. L. K., Bertram, L., Bis, J. C., Burdick, K. E.,
Christoforou, A., DeRosse, P., \ldots{} Kleineidam, L. (2019). Author
Correction: Study of 300,486 individuals identifies 148 independent
genetic loci influencing general cognitive function (Nature
Communications, (2018), 9, 1, (2098), 10.1038/s41467-018-04362-x).
\emph{Nature Communications}, \emph{10}(1).
\url{https://doi.org/10.1038/s41467-019-10160-w}}

\leavevmode\hypertarget{ref-bar-zeev_improving_2019}{}%
\CSLLeftMargin{140. }
\CSLRightInline{Bar-Zeev, Y., Bonevski, B., Lim, L. L., Twyman, L.,
Skelton, E., Gruppetta, M., Palazzi, K., Oldmeadow, C., \& Gould, G. S.
(2019). Improving health providers smoking cessation care in pregnancy:
A systematic review and meta-analysis. \emph{Addictive Behaviors},
\emph{93}, 29--38. \url{https://doi.org/10.1016/j.addbeh.2019.01.002}}

\leavevmode\hypertarget{ref-ferguson_reduced_2019}{}%
\CSLLeftMargin{141. }
\CSLRightInline{Ferguson, J. K., Munnoch, S. A., Kozierowski, K., Chiu,
S., \& Oldmeadow, C. (2019). Reduced VRE and MRSA colonisation and
infection following sustained reduction in broad spectrum antibiotic use
in a large tertiary hospital. \emph{Medical Journal of Australia},
\emph{211}(3), 126--127. \url{https://doi.org/10.5694/mja2.50218}}

\leavevmode\hypertarget{ref-bar-zeev_improving_2019-1}{}%
\CSLLeftMargin{142. }
\CSLRightInline{Bar-Zeev, Y., Bovill, M., Bonevski, B., Gruppetta, M.,
Oldmeadow, C., Palazzi, K., Atkins, L., Reath, J., \& Gould, G. S.
(2019). Improving smoking cessation care in pregnancy at Aboriginal
Medical Services: ICAN QUIT in Pregnancy' step-wedge cluster randomised
study. \emph{BMJ Open}, \emph{9}(6).
\url{https://doi.org/10.1136/bmjopen-2018-025293}}

\leavevmode\hypertarget{ref-searle_calf_2019}{}%
\CSLLeftMargin{143. }
\CSLRightInline{Searle, A., Spink, M. J., Oldmeadow, C., Chiu, S., \&
Chuter, V. H. (2019). Calf muscle stretching is ineffective in
increasing ankle range of motion or reducing plantar pressures in people
with diabetes and ankle equinus: A randomised controlled trial.
\emph{Clinical Biomechanics}, \emph{69}, 52--57.
\url{https://doi.org/10.1016/j.clinbiomech.2019.07.005}}

\leavevmode\hypertarget{ref-beck_adapted_2019}{}%
\CSLLeftMargin{144. }
\CSLRightInline{Beck, A. K., Forbes, E., Baker, A. L., Britton, B.,
Oldmeadow, C., \& Carter, G. (2019). Adapted motivational interviewing
for brief healthcare consultations: Protocol for a systematic review and
meta-analysis of treatment fidelity in real-world evaluations of
behaviour change counselling. \emph{BMJ Open}, \emph{9}(7).
\url{https://doi.org/10.1136/bmjopen-2018-028417}}

\leavevmode\hypertarget{ref-casey_reliability_2019}{}%
\CSLLeftMargin{145. }
\CSLRightInline{Casey, S., Lanting, S., Oldmeadow, C., \& Chuter, V.
(2019). The reliability of the ankle brachial index: A systematic
review. \emph{Journal of Foot and Ankle Research}, \emph{12}(1), 1--10.
\url{https://doi.org/10.1186/s13047-019-0350-1}}

\leavevmode\hypertarget{ref-jones_fdg-pet_2019}{}%
\CSLLeftMargin{146. }
\CSLRightInline{Jones, M. P., Hruby, G., Metser, U., Sridharan, S.,
Capp, A., Kumar, M., Gallagher, S., Rutherford, N., Holder, C.,
Oldmeadow, C., \& Martin, J. (2019). FDG-PET parameters predict for
recurrence in anal cancer - Results from a prospective, multicentre
clinical trial. \emph{Radiation Oncology}, \emph{14}(1).
\url{https://doi.org/10.1186/s13014-019-1342-9}}

\leavevmode\hypertarget{ref-snodgrass_cervical_2019}{}%
\CSLLeftMargin{147. }
\CSLRightInline{Snodgrass, S., Croker, C., Yerrapothu, M., Shepherd, S.,
Stanwell, P., Holder, C., Oldmeadow, C., \& Elliot, J. (2019). Cervical
muscle volume in individuals with idiopathic neck pain compared to
asymptomatic controls: A cross-sectional magnetic resonance imaging
study. \emph{Musculoskeletal Science and Practice}, \emph{44}(In press).
\url{https://doi.org/10.1016/j.msksp.2019.102050}}

\leavevmode\hypertarget{ref-lee_relationship_2019}{}%
\CSLLeftMargin{148. }
\CSLRightInline{Lee, Y. Q., Lumbers, E. R., Oldmeadow, C., Collins, C.
E., Johnson, V., Keogh, L., Sutherland, K., Gordon, A., Smith, R., Rae,
K. M., \& Pringle, K. G. (2019). The relationship between maternal
adiposity during pregnancy and fetal kidney development and kidney
function in infants: The Gomeroi gaaynggal study. \emph{Physiological
Reports}, \emph{7}(17), 1--14.
\url{https://doi.org/10.14814/phy2.14227}}

\leavevmode\hypertarget{ref-sutherland_protocol_2019}{}%
\CSLLeftMargin{149. }
\CSLRightInline{Sutherland, R., Brown, A., Nathan, N., Janssen, L.,
Reynolds, R., Walton, A., Hudson, N., Chooi, A., Yoong, S., Wiggers, J.,
Bailey, A., Evans, N., Gillham, K., Oldmeadow, C., Searles, A., Reeves,
P., Rissel, C., Davies, M., Reilly, K., \ldots{} Wolfenden, L. (2019).
Protocol for an effectiveness- implementation hybrid trial to assess the
effectiveness and cost-effectiveness of an m-health intervention to
decrease the consumption of discretionary foods packed in school
lunchboxes: The 'SWAP IT' trial. \emph{BMC Public Health}, \emph{19}(1),
1510. \url{https://doi.org/10.1186/s12889-019-7725-x}}

\leavevmode\hypertarget{ref-hasnain_can_2019}{}%
\CSLLeftMargin{150. }
\CSLRightInline{Hasnain, M. G., Levi, C. R., Ryan, A., Hubbard, I. J.,
Hall, A., Oldmeadow, C., Grady, A., Jayakody, A., Attia, J. R., \& Paul,
C. L. (2019). Can a multicomponent multidisciplinary implementation
package change physicians' and nurses' perceptions and practices
regarding thrombolysis for acute ischemic stroke? An exploratory
analysis of a cluster-randomized trial. \emph{Implementation Science},
\emph{14}(1). \url{https://doi.org/10.1186/s13012-019-0940-0}}

\leavevmode\hypertarget{ref-denham_development_2019}{}%
\CSLLeftMargin{151. }
\CSLRightInline{Denham, A. M. J., Guillaumier, A., McCrabb, S., Turner,
A., Baker, A. L., Spratt, N. J., Pollack, M., Magin, P., Oldmeadow, C.,
Collins, C., Callister, R., Wallis, M., Wynne, O., \& Bonevski, B.
(2019). Development of an online secondary prevention programme for
stroke survivors: Prevent 2nd Stroke. \emph{BMJ Innovations},
\emph{5}(1), 35--42. \url{https://doi.org/10.1136/bmjinnov-2017-000257}}

\leavevmode\hypertarget{ref-burgess_eligibility_2019}{}%
\CSLLeftMargin{152. }
\CSLRightInline{Burgess, A., Goon, K., Brannan, J. D., Attia, J.,
Palazzi, K., Oldmeadow, C., Corte, T. J., Glaspole, I., Goh, N., Keir,
G., Allan, H., Chapman, S., Cooper, W., Ellis, S., Hopkins, P., Moodley,
Y., Reynolds, P., Zappala, C., Macansh, S., \& Grainge, C. (2019).
Eligibility for anti-fibrotic treatment in idiopathic pulmonary fibrosis
depends on the predictive equation used for pulmonary function testing.
\emph{Respirology}, \emph{24}(10), 988--995.
\url{https://doi.org/10.1111/resp.13540}}

\leavevmode\hypertarget{ref-vandelanotte_more_2019}{}%
\CSLLeftMargin{153. }
\CSLRightInline{Vandelanotte, C., Duncan, M. J., Kolt, G. S.,
Caperchione, C. M., Savage, T. N., Van Itallie, A., Oldmeadow, C.,
Alley, S. J., Tague, R., Maeder, A. J., Rosenkranz, R. R., \& Mummery,
W. K. (2019). More real-world trials are needed to establish if
web-based physical activity interventions are effective. \emph{British
Journal of Sports Medicine}, \emph{53}(24), 1553--1554.
\url{https://doi.org/10.1136/bjsports-2018-099437}}

\leavevmode\hypertarget{ref-beaudry-bellefeuille_toileting_2019}{}%
\CSLLeftMargin{154. }
\CSLRightInline{Beaudry-Bellefeuille, I., Lane, A., Chiu, S., Oldmeadow,
C., Ramos Polo, E., \& Lane, S. J. (2019). The Toileting Habit Profile
Questionnaire-Revised: Examining Discriminative and Concurrent Validity.
\emph{Journal of Occupational Therapy, Schools, and Early Intervention},
\emph{12}(3), 311--322.
\url{https://doi.org/10.1080/19411243.2019.1590756}}

\leavevmode\hypertarget{ref-hobden_prevalence_2020-1}{}%
\CSLLeftMargin{155. }
\CSLRightInline{Hobden, B., Bryant, J., Forshaw, K., Oldmeadow, C.,
Evans, T. J., \& Sanson-Fisher, R. (2020). Prevalence and
characteristics associated with concurrent smoking and alcohol misuse
within Australian general practice patients. \emph{Australian Health
Review}, \emph{44}(1), 125--131. \url{https://doi.org/10.1071/AH18126}}

\leavevmode\hypertarget{ref-kelly_study_2020}{}%
\CSLLeftMargin{156. }
\CSLRightInline{Kelly, P., Deane, F., Byrne, G., Degan, T., Osborne, B.,
Townsend, C., McKay, J., Robinson, L., Oldmeadow, C., Lawson, K.,
Searles, A., \& Lunn, J. (2020). Study protocol the Continuing Care
Project: A randomised controlled trial of a continuing care telephone
intervention following residential substance dependence treatment.
\emph{BMC Public Health}, \emph{20}(1).
\url{https://doi.org/10.1186/s12889-020-8206-y}}

\leavevmode\hypertarget{ref-troy_diagnostic_2020}{}%
\CSLLeftMargin{157. }
\CSLRightInline{Troy, L. K., Grainge, C., Corte, T. J., Williamson, J.
P., Vallely, M. P., Cooper, W. A., Mahar, A., Myers, J. L., Lai, S.,
Mulyadi, E., Torzillo, P. J., Phillips, M. J., Jo, H. E., Webster, S.
E., Lin, Q. T., Rhodes, J. E., Salamonsen, M., Wrobel, J. P., Harris,
B., \ldots{} Twaddell, S. (2020). Diagnostic accuracy of transbronchial
lung cryobiopsy for interstitial lung disease diagnosis (COLDICE): A
prospective, comparative study. \emph{The Lancet Respiratory Medicine},
\emph{8}(2), 171--181.
\url{https://doi.org/10.1016/S2213-2600(19)30342-X}}

\leavevmode\hypertarget{ref-stuart_psychological_2020}{}%
\CSLLeftMargin{158. }
\CSLRightInline{Stuart, A. M., Baker, A. L., Denham, A. M. J., Lee, N.
K., Hall, A., Oldmeadow, C., Dunlop, A., Bowman, J., \& McCarter, K.
(2020). Psychological treatment for methamphetamine use and associated
psychiatric symptom outcomes: A systematic review. \emph{Journal of
Substance Abuse Treatment}, \emph{109}, 61--79.
\url{https://doi.org/10.1016/j.jsat.2019.09.005}}

\leavevmode\hypertarget{ref-kelly_erratum_2020}{}%
\CSLLeftMargin{159. }
\CSLRightInline{Kelly, P., Deane, F., Baker, A., Byrne, G., Degan, T.,
Osborne, B., Townsend, C., McKay, J., Robinson, L., Oldmeadow, C.,
Lawson, K., Searles, A., \& Lunn, J. (2020). Erratum: Correction to:
Study protocol the Continuing Care Project: A randomised controlled
trial of a continuing care telephone intervention following residential
substance dependence treatment (BMC public health (2020) 20 1 (107)).
\emph{BMC Public Health}, \emph{20}(1), 258.
\url{https://doi.org/10.1186/s12889-020-8328-2}}

\leavevmode\hypertarget{ref-joseph_radiation_2020}{}%
\CSLLeftMargin{160. }
\CSLRightInline{Joseph, D., Denham, J. W., Steigler, A., Lamb, D. S.,
Spry, N. A., Stanley, J., Shannon, T., Duchesne, G., Atkinson, C.,
Matthews, J. H. L., Turner, S., Kenny, L., Christie, D., Tai, K. H.,
Gogna, N. K., Kearvell, R., Murray, J., Ebert, M. A., Haworth, A.,
\ldots{} Attia, J. (2020). Radiation Dose Escalation or Longer Androgen
Suppression to Prevent Distant Progression in Men With Locally Advanced
Prostate Cancer: 10-Year Data From the TROG 03.04 RADAR Trial.
\emph{International Journal of Radiation Oncology Biology Physics},
\emph{106}(4), 693--702.
\url{https://doi.org/10.1016/j.ijrobp.2019.11.415}}

\leavevmode\hypertarget{ref-delahunt_perineural_2020}{}%
\CSLLeftMargin{161. }
\CSLRightInline{Delahunt, B., Murray, J. D., Steigler, A., Atkinson, C.,
Christie, D., Duchesne, G., Egevad, L., Joseph, D., Matthews, J.,
Oldmeadow, C., Samaratunga, H., Spry, N. A., Srigley, J. R.,
Hondermarck, H., \& Denham, J. W. (2020). Perineural invasion by
prostate adenocarcinoma in needle biopsies predicts bone metastasis: Ten
year data from the TROG 03.04 RADAR Trial. \emph{Histopathology},
\emph{Print-Electronic}. \url{https://doi.org/10.1111/his.14107}}

\leavevmode\hypertarget{ref-jackson_better_2020}{}%
\CSLLeftMargin{162. }
\CSLRightInline{Jackson, J. K., MacDonald-Wicks, L. K., McEvoy, M. A.,
Forder, P. M., Holder, C., Oldmeadow, C., Byles, J. E., \& Patterson, A.
J. (2020). Better diet quality scores are associated with a lower risk
of hypertension and non-fatal CVD in middle-aged Australian women over
15 years of follow-up. \emph{Public Health Nutrition}, \emph{23}(5),
882--893. \url{https://doi.org/10.1017/S1368980019002842}}

\leavevmode\hypertarget{ref-phad_dilated_2020}{}%
\CSLLeftMargin{163. }
\CSLRightInline{Phad, N. S., Waal, K. de, Holder, C., \& Oldmeadow, C.
(2020). Dilated hypertrophy: A distinct pattern of cardiac remodeling in
preterm infants. \emph{Pediatric Research}, \emph{87}(1), 146--152.
\url{https://doi.org/10.1038/s41390-019-0568-4}}

\leavevmode\hypertarget{ref-english_breaking_2018}{}%
\CSLLeftMargin{164. }
\CSLRightInline{English, C., Janssen, H., Crowfoot, G., Callister, R.,
Dunn, A., Mackie, P., Oldmeadow, C., Ong, L. K., Palazzi, K., Patterson,
A. J., Spratt, N. J., Walker, F. R., Bernhardt, J., \& Dunstan, D. W.
(2018). Breaking up sitting time after stroke (BUST-stroke).
\emph{International Journal of Stroke}, \emph{13}(9), 921--931.
\url{https://doi.org/10.1177/1747493018801222}}

\leavevmode\hypertarget{ref-ranasinghe_bladder_2013}{}%
\CSLLeftMargin{165. }
\CSLRightInline{Ranasinghe, W. K. B., Attia, J., Oldmeadow, C.,
Lawrentschuk, N., Robertson, J., Ranasinghe, T., Bolton, D., \& Persad,
R. (2013). Bladder carcinoma in situ (CIS) in Australia: A rising
incidence for an under-reported malignancy. \emph{BJU International},
\emph{112}(S2), 46--52. \url{https://doi.org/10.1111/bju.12052}}

\leavevmode\hypertarget{ref-sprott_assessment_2019}{}%
\CSLLeftMargin{166. }
\CSLRightInline{Sprott, P., Hibberd, A. D., Heer, M. K., Trevillian, P.
R., Clark, D. A., Johnson, D. W., Oldmeadow, C., Chiu, S., \& Attia, J.
R. (2019). Assessment of Restored Kidney Transplantation Including the
Use of Wider Criteria for Accepting Renal Donors After Cancer Excision.
\emph{Transplantation Direct}, \emph{5}(11).
\url{https://doi.org/10.1097/TXD.0000000000000946}}

\leavevmode\hypertarget{ref-lynagh_rct_2012}{}%
\CSLLeftMargin{167. }
\CSLRightInline{Lynagh, M. C., Bonevski, B., Sanson-Fisher, R. W.,
Symonds, I. M., Scott, A., Hall, A. E., \& Oldmeadow, C. J. (2012). An
RCT protocol of varying financial incentive amounts for smoking
cessation among pregnant women. \emph{BMC Public Health}, \emph{12},
1032.}

\leavevmode\hypertarget{ref-guillaumier_online_2019}{}%
\CSLLeftMargin{168. }
\CSLRightInline{Guillaumier, A., McCrabb, S., Spratt, N. J., Pollack,
M., Baker, A. L., Magin, P., Turner, A., Oldmeadow, C., Collins, C.,
Callister, R., Levi, C., Searles, A., Deeming, S., Wynne, O., Denham, A.
M. J., Clancy, B., \& Bonevski, B. (2019). An online intervention for
improving stroke survivors' health-related quality of life: Study
protocol for a randomised controlled trial. \emph{Trials}, \emph{20}(1).
\url{https://doi.org/10.1186/s13063-019-3604-0}}

\leavevmode\hypertarget{ref-holliday_examination_2013}{}%
\CSLLeftMargin{169. }
\CSLRightInline{Holliday, S., Magin, P., Oldmeadow, C., Attia, J.,
Dunbabin, J., Henry, J., Lintzeris, N., Goode, S., \& Dunlop, A. (2013).
An examination of the influences on New South Wales general
practitioners regarding the provision of opioid substitution therapy.
\emph{Drug and Alcohol Review}, \emph{32}(5), 495--503.
\url{https://doi.org/10.1111/dar.12046}}

\leavevmode\hypertarget{ref-holliday_evaluation_2013}{}%
\CSLLeftMargin{170. }
\CSLRightInline{Holliday, S., Magin, P., Dunbabin, J., Oldmeadow, C.,
Henry, J. M., Lintzeris, N., Attia, J., Goode, S., \& Dunlop, A. (2013).
An Evaluation of the Prescription of Opioids for Chronic Nonmalignant
Pain by Australian General Practitioners. \emph{Pain Medicine (United
States)}, \emph{14}(1), 62--74.
\url{https://doi.org/10.1111/j.1526-4637.2012.01527.x}}

\leavevmode\hypertarget{ref-sinclair_evaluation_2019}{}%
\CSLLeftMargin{171. }
\CSLRightInline{Sinclair, P. M., Kable, A., Levett-Jones, T., Holder,
C., \& Oldmeadow, C. J. (2019). An evaluation of general practice
nurses' knowledge of chronic kidney disease risk factors and screening
practices following completion of a case study-based asynchronous
e-learning module. \emph{Australian Journal of Primary Health},
\emph{25}(4), 346--352. \url{https://doi.org/10.1071/PY18173}}

\leavevmode\hypertarget{ref-kable_evaluation_2019}{}%
\CSLLeftMargin{172. }
\CSLRightInline{Kable, A., Pond, D., Hullick, C., Chenoweth, L., Duggan,
A., Attia, J., \& Oldmeadow, C. (2019). An evaluation of discharge
documentation for people with dementia discharged home from hospital --
A cross-sectional pilot study. \emph{Dementia}, \emph{18}(5),
1764--1776. \url{https://doi.org/10.1177/1471301217728845}}

\leavevmode\hypertarget{ref-bovill_aboriginal_2020}{}%
\CSLLeftMargin{173. }
\CSLRightInline{Bovill, M., Bar-Zeev, Y., Bonevski, B., Gruppetta, M.,
Oldmeadow, C., Hall, A., Reath, J., \& Gould, G. S. (2020). Aboriginal
Wingadhan Birrang (woman's journey) of smoking cessation during
pregnancy as they participate in the ICAN QUIT in pregnancy pilot
step-wedge trial. \emph{Women and Birth}, \emph{33}(3), 300--308.
\url{https://doi.org/10.1016/j.wombi.2019.05.003}}

\leavevmode\hypertarget{ref-sutherland_cluster_2019}{}%
\CSLLeftMargin{174. }
\CSLRightInline{Sutherland, R., Campbell, E., Nathan, N., Wolfenden, L.,
Lubans, D. R., Morgan, P. J., Gillham, K., Oldmeadow, C., Searles, A.,
Reeves, P., Williams, M., Evans, N., Bailey, A., Morrison, R.,
McLaughlin, M., \& Wiggers, J. (2019). A cluster randomised trial of an
intervention to increase the implementation of physical activity
practices in secondary schools: Study protocol for scaling up the
Physical Activity 4 Everyone (PA4E1) program. \emph{BMC Public Health},
\emph{19}(1). \url{https://doi.org/10.1186/s12889-019-6965-0}}

\leavevmode\hypertarget{ref-hutchesson_targeted_2018}{}%
\CSLLeftMargin{175. }
\CSLRightInline{Hutchesson, M., Callister, R., Morgan, P., Pranata, I.,
Clarke, E., Skinner, G., Ashton, L., Whatnall, M., Jones, M., Oldmeadow,
C., \& Collins, C. (2018). A Targeted and Tailored eHealth Weight Loss
Program for Young Women: The Be Positive Be Healthe Randomized
Controlled Trial. \emph{Healthcare}, \emph{6}(2), 1--19.
\url{https://doi.org/10.3390/healthcare6020039}}

\leavevmode\hypertarget{ref-hasnain_thrombolysis_2020}{}%
\CSLLeftMargin{176. }
\CSLRightInline{Hasnain, M. G., Paul, C. L., Attia, J. R., Ryan, A.,
Kerr, E., Oldmeadow, C., D'Este, C. A., Bivard, A., Hubbard, I. J.,
Milton, A. H., \& Levi, C. R. (2020). Thrombolysis implementation
intervention and clinical outcome: A secondary analysis of a cluster
randomized trial. \emph{BMC Cardiovascular Disorders}, \emph{20}(1),
432. \url{https://doi.org/10.1186/s12872-020-01705-9}}

\leavevmode\hypertarget{ref-lim_systematic_2017}{}%
\CSLLeftMargin{177. }
\CSLRightInline{Lim, M. S., Ariyarajah, A., Oldmeadow, C., Hall, A., \&
Enjeti, A. K. (2017). A Systematic Review and Meta-analysis Comparing
Anticoagulation versus No Anticoagulation and Shorter versus Longer
duration of Anticoagulation for Treatment of Isolated Distal Deep Vein
Thrombosis. \emph{Seminars in Thrombosis and Hemostasis}, \emph{43}(8),
836--848. \url{https://doi.org/10.1055/s-0037-1604085}}

\leavevmode\hypertarget{ref-iseme_role_2017}{}%
\CSLLeftMargin{178. }
\CSLRightInline{Iseme, R. A., McEvoy, M., Kelly, B., Agnew, L., Walker,
F. R., Handley, T., Oldmeadow, C., Attia, J., \& Boyle, M. (2017). A
role for autoantibodies in atherogenesis. \emph{Cardiovascular
Research}, \emph{113}(10), 1102--1112.
\url{https://doi.org/10.1093/cvr/cvx112}}

\leavevmode\hypertarget{ref-jones_prospective_2020}{}%
\CSLLeftMargin{179. }
\CSLRightInline{Jones, M., Hruby, G., Coolens, C., Driscoll, B.,
Stanwell, P., Kumar, M., Capp, A., Sridharan, S., Arm, J., Gallagher,
S., Holder, C., Oldmeadow, C., \& Martin, J. (2020). A prospective,
multi-centre trial of multi-parametric MRI as a biomarker in anal
carcinoma. \emph{Radiotherapy and Oncology}, \emph{144}, 7--12.
\url{https://doi.org/10.1016/j.radonc.2019.10.001}}

\leavevmode\hypertarget{ref-stevenson_multi-center_2020}{}%
\CSLLeftMargin{180. }
\CSLRightInline{Stevenson, W., Bryant, J., Watson, R., Sanson-Fisher,
R., Oldmeadow, C., Henskens, F., Brown, C., Ramanathan, S., Tiley, C.,
Enjeti, A., Guest, J., Tzelepis, F., Paul, C., \& D'Este, C. (2020). A
multi-center randomized controlled trial to reduce unmet needs,
depression, and anxiety among hematological cancer patients and their
support persons. \emph{Journal of Psychosocial Oncology}, \emph{38}(3),
272--292. \url{https://doi.org/10.1080/07347332.2019.1692991}}

\leavevmode\hypertarget{ref-de_vries_meta-analysis_2016}{}%
\CSLLeftMargin{181. }
\CSLRightInline{De Vries, P. S., Chasman, D. I., Sabater-Lleal, M.,
Chen, M. H., Huffman, J. E., Steri, M., Tang, W., Teumer, A., Marioni,
R. E., Grossmann, V., Hottenga, J. J., Trompet, S., Müller-Nurasyid, M.,
Zhao, J. H., Brody, J. A., Kleber, M. E., Guo, X., Wang, J. J., Auer, P.
L., \ldots{} Franco, O. H. (2016). A meta-analysis of 120 246
individuals identifies 18 new loci for fibrinogen concentration.
\emph{Human Molecular Genetics}, \emph{25}(2), 358--370.
\url{https://doi.org/10.1093/hmg/ddv454}}

\leavevmode\hypertarget{ref-noble_cross-sectional_2015}{}%
\CSLLeftMargin{182. }
\CSLRightInline{Noble, N. E., Paul, C. L., Turner, N., Blunden, S. V.,
Oldmeadow, C., \& Turon, H. E. (2015). A cross-sectional survey and
latent class analysis of the prevalence and clustering of health risk
factors among people attending an Aboriginal Community Controlled Health
Service. \emph{BMC Public Health}, \emph{15}(1).
\url{https://doi.org/10.1186/s12889-015-2015-8}}

\leavevmode\hypertarget{ref-nathan_cluster_2019}{}%
\CSLLeftMargin{183. }
\CSLRightInline{Nathan, N., Wiggers, J., Bauman, A. E., Rissel, C.,
Searles, A., Reeves, P., Oldmeadow, C., Naylor, P. J., Cradock, A. L.,
Sutherland, R., Gillham, K., Duggan, B., Chad, S., McCarthy, N.,
Pettett, M., Jackson, R., Reilly, K., Herrmann, V., Hope, K., \ldots{}
Wolfenden, L. (2019). A cluster randomised controlled trial of an
intervention to increase the implementation of school physical activity
policies and guidelines: Study protocol for the physically active
children in education (PACE) study. \emph{BMC Public Health},
\emph{19}(1). \url{https://doi.org/10.1186/s12889-019-6492-z}}

\leavevmode\hypertarget{ref-paul_staff_2019}{}%
\CSLLeftMargin{184. }
\CSLRightInline{Paul, C., D'Este, C., Ryan, A., Jayakody, A., Attia, J.,
Oldmeadow, C., Kerr, E., Henskens, F., Grady, A., \& Levi, C. R. (2019).
Staff perspectives from Australian hospitals seeking to improve
implementation of thrombolysis care for acute stroke. \emph{SAGE OPEN
MEDICINE}, \emph{7}(UNSP 2050312119865656).
\url{https://doi.org/10.1177/2050312119865656}}

\leavevmode\hypertarget{ref-oldmeadow_heritability_2009}{}%
\CSLLeftMargin{185. }
\CSLRightInline{Oldmeadow, C. J., Mengersen, K., Martin, N., \& Duffy,
D. L. (2009). Heritability and linkage analysis of appendicitis
utilizing age at onset. \emph{Twin Research and Human Genetics},
\emph{12}(2), 150--157. \url{https://doi.org/10.1375/twin.12.2.150}}

\leavevmode\hypertarget{ref-okada_meta-analysis_2012}{}%
\CSLLeftMargin{186. }
\CSLRightInline{Okada, Y., Sim, X., Go, M. J., Wu, J.-Y., Gu, D.,
Takeuchi, F., Takahashi, A., Maeda, S., Tsunoda, T., Chen, P., Lim,
S.-C., Wong, T.-Y., Liu, J., Young, T. L., Aung, T., Seielstad, M., Teo,
Y.-Y., Kim, Y. J., Lee, J.-Y., \ldots{} Attia, J. R. (2012).
Meta-analysis identifies multiple loci associated with kidney
function-related traits in east Asian populations. \emph{Nature
Genetics}, \emph{44}(8), 904--909.}

\leavevmode\hypertarget{ref-collins_percutaneous_2012}{}%
\CSLLeftMargin{187. }
\CSLRightInline{Collins, N. J., Hatton, R., Ng, K., Bhagwandeen, R.,
Attia, J. R., Oldmeadow, C. J., \& Jayasinghe, R. (2012). Percutaneous
device closure of patent foramen ovale using the premere occlusion
device: Initial experience, procedural, and intermediate-term results.
\emph{Journal of Invasive Cardiology}, \emph{24}(4), 164--168.}

\leavevmode\hypertarget{ref-kottgen_genome-wide_2013}{}%
\CSLLeftMargin{188. }
\CSLRightInline{Kottgen, A., Albrecht, E., Teumer, A., Vitart, V.,
Krumsiek, J., Hundertmark, C., Pistis, G., Ruggiero, D., O'Seaghdha, C.
M., Haller, T., Yang, Q., Tanaka, T., Johnson, A. D., Kutalik, Z.,
Smith, A. V., Shi, J., Struchalin, M., Middelberg, R. P. S., Brown, M.
J., \ldots{} Al, E. (2013). Genome-wide association analyses identify 18
new loci associated with serum urate concentrations. \emph{Nature
Genetics}, \emph{45}(2), 145--154.}

\leavevmode\hypertarget{ref-rietveld_gwas_2013}{}%
\CSLLeftMargin{189. }
\CSLRightInline{Rietveld, C. A., Medland, S. E., Derringer, J., Yang,
J., Esko, T., Martin, N. W., Westra, H.-J., Shakhbazov, K., Abdellaoui,
A., Agrawal, A., Albrecht, E., Alizadeh, B. Z., Amin, N., Barnard, J.,
Baumeister, S. E., Benke, K. S., Bielak, L. F., Boatman, J. A., Boyle,
P. A., \ldots{} Al, E. (2013). GWAS of 126,559 individuals identifies
genetic variants associated with educational attainment. \emph{Science},
\emph{340}(6139), 1467--1471.}

\leavevmode\hypertarget{ref-gunathilake_mild_2013}{}%
\CSLLeftMargin{190. }
\CSLRightInline{Gunathilake, R., Oldmeadow, C., McEvoy, M., Kelly, B.,
Inder, K., Schofield, P., \& Attia, J. (2013). Mild Hyponatremia Is
Associated With Impaired Cognition And Falls In Community-Dwelling Older
Persons. \emph{Journal of the American Geriatrics Society},
\emph{61}(10), 1838--1839. \url{https://doi.org/10.1111/jgs.12468}}

\leavevmode\hypertarget{ref-williams_changes_2013}{}%
\CSLLeftMargin{191. }
\CSLRightInline{Williams, N., Hardy, B. M., Tarrant, S., Enninghorst,
N., Attia, J., Oldmeadow, C., \& Balogh, Z. J. (2013). Changes in hip
fracture incidence, mortality and length of stay over the last decade in
an Australian major trauma centre. \emph{Archives of Osteoporosis},
\emph{8}(1-2). \url{https://doi.org/10.1007/s11657-013-0150-3}}

\leavevmode\hypertarget{ref-mccarthy-jones_preliminary_2014}{}%
\CSLLeftMargin{192. }
\CSLRightInline{McCarthy-Jones, S., Green, M. J., Scott, R. J., Tooney,
P. A., Cairns, M. J., Wu, J. Q., Oldmeadow, C., \& Carr, V. (2014).
Preliminary evidence of an interaction between the FOXP2 gene and
childhood emotional abuse predicting likelihood of auditory verbal
hallucinations in schizophrenia. \emph{Journal of Psychiatric Research},
\emph{50}(1), 66--72.
\url{https://doi.org/10.1016/j.jpsychires.2013.11.012}}

\leavevmode\hypertarget{ref-rifat_development_2014}{}%
\CSLLeftMargin{193. }
\CSLRightInline{Rifat, M., Milton, A. H., Hall, J., Oldmeadow, C.,
Islam, M. A., Husain, A., Akhanda, M. W., \& Siddiquea, B. N. (2014).
Development of multidrug resistant tuberculosis in Bangladesh: A
case-control study on risk factors. \emph{PLoS ONE}, \emph{9}(8).
\url{https://doi.org/10.1371/journal.pone.0105214}}

\leavevmode\hypertarget{ref-de_zeeuw_polygenic_2014}{}%
\CSLLeftMargin{194. }
\CSLRightInline{Zeeuw, E. L. de, Beijsterveldt, C. E. M. van, Glasner,
T. J., Bartels, M., Ehli, E. A., Davies, G. E., Hudziak, J. J.,
Rietveld, C. A., Groen-Blokhuis, M. M., Hottenga, J. J., Geus, E. J. C.
de, Boomsma, D. I., Abdellaoui, A., Agrawal, A., Albrecht, E., Alizadeh,
B. Z., Allik, J., Amin, N., Attia, J. R., \ldots{} Joshi, P. K. (2014).
Polygenic scores associated with educational attainment in adults
predict educational achievement and ADHD symptoms in children.
\emph{American Journal of Medical Genetics, Part B: Neuropsychiatric
Genetics}, \emph{165}(6), 510--520.
\url{https://doi.org/10.1002/ajmg.b.32254}}

\leavevmode\hypertarget{ref-george_risk_2014}{}%
\CSLLeftMargin{195. }
\CSLRightInline{George, M., Asab, N. A., Varughese, E., Irwin, M.,
Oldmeadow, C., Hollebone, K., Apen, K., \& Renner, S. (2014). Risk
awareness on uterine cancer among Australian women. \emph{Asian Pacific
Journal of Cancer Prevention}, \emph{15}(23), 10251--10254.
\url{https://doi.org/10.7314/APJCP.2014.15.23.10251}}

\leavevmode\hypertarget{ref-abdullah_architecture_2014}{}%
\CSLLeftMargin{196. }
\CSLRightInline{Abdullah, N., Attia, J., Oldmeadow, C., Scott, R. J., \&
Holliday, E. G. (2014). The architecture of risk for type 2 diabetes:
Understanding asia in the context of global findings.
\emph{International Journal of Endocrinology}, \emph{2014}.
\url{https://doi.org/10.1155/2014/593982}}

\leavevmode\hypertarget{ref-napthali_thyroid_2014}{}%
\CSLLeftMargin{197. }
\CSLRightInline{Napthali, K., Boyle, M., Tran, H., Schofield, P. W.,
Peel, R., McEvoy, M., Oldmeadow, C., \& Attia, J. (2014). Thyroid
Antibodies, Autoimmunity and Cognitive Decline: Is There a
Population-Based Link? \emph{DEMENTIA AND GERIATRIC COGNITIVE DISORDERS
EXTRA}, \emph{4}(2), 140--146. \url{https://doi.org/10.1159/000362716}}

\leavevmode\hypertarget{ref-moayyeri_genetic_2014}{}%
\CSLLeftMargin{198. }
\CSLRightInline{Moayyeri, A., Hsu, Y. H., Karasik, D., Estrada, K.,
Xiao, S. M., Nielson, C., Srikanth, P., Giroux, S., Wilson, S. G.,
Zheng, H. F., Smith, A. V., Pye, S. R., Leo, P. J., Teumer, A., Hwang,
J. Y., Ohlsson, C., McGuigan, F., Minster, R. L., Hayward, C., \ldots{}
Lorenc, R. S. (2014). Genetic determinants of heel bone properties:
Genome-wide association meta-analysis and replication in the
GEFOS/GENOMOS consortium. \emph{Human Molecular Genetics},
\emph{23}(11), 3054--3068. \url{https://doi.org/10.1093/hmg/ddt675}}

\leavevmode\hypertarget{ref-denham_short-term_2014}{}%
\CSLLeftMargin{199. }
\CSLRightInline{Denham, J. W., Joseph, D., Lamb, D. S., Spry, N. A.,
Duchesne, G., Matthews, J., Atkinson, C., Tai, K. H., Christie, D., \&
Kenny, L. (2014). Short-term androgen suppression and radiotherapy
versus intermediate-term androgen suppression and radiotherapy, with or
without zoledronic acid, in men with locally advanced prostate cancer
(TROG 03.04 RADAR): An open-label, randomised, phase 3 factorial trial.
\emph{The Lancet Oncology}, \emph{15}(10), 1076--1089.
\url{https://doi.org/10.1016/S1470-2045(14)70328-6}}

\leavevmode\hypertarget{ref-loth_genome-wide_2014}{}%
\CSLLeftMargin{200. }
\CSLRightInline{Loth, D. W., Artigas, M. S., Gharib, S. A., Wain, L. V.,
Franceschini, N., Koch, B., Pottinger, T. D., Smith, A. V., Duan, Q., \&
Oldmeadow, C. (2014). Genome-wide association analysis identifies six
new loci associated with forced vital capacity. \emph{Nature Genetics},
\emph{46}(7), 669--677. \url{https://doi.org/10.1038/ng.3011}}

\leavevmode\hypertarget{ref-holliday_polygenic_2014}{}%
\CSLLeftMargin{201. }
\CSLRightInline{Holliday, E. G., Traylor, M., Malik, R., Bevan, S.,
Maguire, J., Koblar, S. A., Sturm, J., Hankey, G. J., Oldmeadow, C.,
McEvoy, M., Sudlow, C., Rothwell, P. M., Coresh, J., Hamet, P.,
Tremblay, J., Turner, S. T., De Andrade, M., Rao, M., Schmidt, R.,
\ldots{} Markus, H. S. (2014). Polygenic overlap between kidney function
and large artery atherosclerotic stroke. \emph{Stroke}, \emph{45}(12),
3508--3513. \url{https://doi.org/10.1161/STROKEAHA.114.006609}}

\leavevmode\hypertarget{ref-morgan_-consultation_2015}{}%
\CSLLeftMargin{202. }
\CSLRightInline{Morgan, S., Wearne, S., Tapley, A., Henderson, K.,
Oldmeadow, C., Ball, J., Driel, M. V., Scott, J., Spike, N., McArthur,
L., \& Magin, P. (2015). In-consultation information and adviceseeking
by Australian GP trainees from GP trainers a cross-sectional analysis.
\emph{Education for Primary Care}, \emph{26}(3), 155--165.
\url{https://doi.org/10.1080/14739879.2015.11494335}}

\leavevmode\hypertarget{ref-thomson_prevalence_2015}{}%
\CSLLeftMargin{203. }
\CSLRightInline{Thomson, A., Morgan, S., Tapley, A., Driel, M. van,
Henderson, K., Oldmeadow, C., Ball, J., Spike, N., McArthur, L., O'Mara,
P., Scott, J., \& Magin, P. (2015). Prevalence and associations of
gender concordance in general practice consultations: A cross-sectional
analysis. \emph{European Journal for Person Centered Healthcare},
\emph{3}(4), 470--477. \url{https://doi.org/10.5750/ejpch.v3i4.1016}}

\leavevmode\hypertarget{ref-debette_genome-wide_2015}{}%
\CSLLeftMargin{204. }
\CSLRightInline{Debette, S., Ibrahim Verbaas, C. A., Bressler, J.,
Schuur, M., Smith, A., Bis, J. C., Davies, G., Wolf, C., Gudnason, V.,
Chibnik, L. B., Yang, Q., DeStefano, A. L., De Quervain, D. J. F.,
Srikanth, V., Lahti, J., Grabe, H. J., Smith, J. A., Priebe, L., Yu, L.,
\ldots{} Garcia, M. (2015). Genome-wide studies of verbal declarative
memory in nondemented older people: The Cohorts for Heart and Aging
Research in Genomic Epidemiology Consortium. \emph{Biological
Psychiatry}, \emph{77}(8), 749--763.
\url{https://doi.org/10.1016/j.biopsych.2014.08.027}}

\leavevmode\hypertarget{ref-sales_quality_2015}{}%
\CSLLeftMargin{205. }
\CSLRightInline{Sales, M., Quain, D., Lasserson, D., Levi, C.,
Oldmeadow, C., Jiwa, M., Parsons, M., Russell, M., Clarey, J., \& Magin,
P. (2015). Quality of referrals and guideline compliance for time to
consultation at an acute neurovascular clinic. \emph{Journal of Stroke
and Cerebrovascular Diseases}, \emph{24}(4), 874--880.
\url{https://doi.org/10.1016/j.jstrokecerebrovasdis.2014.12.004}}

\leavevmode\hypertarget{ref-holliday_genetic_2015}{}%
\CSLLeftMargin{206. }
\CSLRightInline{Holliday, E. G., Traylor, M., Malik, R., Bevan, S.,
Falcone, G., Hopewell, J. C., Cheng, Y. C., Cotlarciuc, I., Bis, J. C.,
Boerwinkle, E., Boncoraglio, G. B., Clarke, R., Cole, J. W., Fornage,
M., Furie, K. L., Ikram, M. A., Jannes, J., Kittner, S. J., Lincz, L.
F., \ldots{} Wray, N. R. (2015). Genetic overlap between diagnostic
subtypes of ischemic stroke. \emph{Stroke}, \emph{46}(3), 615--619.
\url{https://doi.org/10.1161/STROKEAHA.114.007930}}

\leavevmode\hypertarget{ref-davies_genetic_2015}{}%
\CSLLeftMargin{207. }
\CSLRightInline{Davies, G., Armstrong, N., Bis, J. C., Bressler, J.,
Chouraki, V., Giddaluru, S., Hofer, E., Ibrahim-Verbaas, C. A., Kirin,
M., \& Lahti, J. (2015). Genetic contributions to variation in general
cognitive function: A meta-analysis of genome-wide association studies
in the CHARGE consortium (N=53 949). \emph{Molecular Psychiatry},
\emph{20}(2), 183--192. \url{https://doi.org/10.1038/mp.2014.188}}

\leavevmode\hypertarget{ref-denham_radiation_2015}{}%
\CSLLeftMargin{208. }
\CSLRightInline{Denham, J. W., Steigler, A., Joseph, D., Lamb, D. S.,
Spry, N. A., Duchesne, G., Atkinson, C., Matthews, J., Turner, S.,
Kenny, L., Tai, K.-H., Gogna, N. K., Gill, S., Tan, H., Kearvell, R.,
Murray, J., Ebert, M., Haworth, A., Kennedy, A., \ldots{} Attia, J.
(2015). Radiation dose escalation or longer androgen suppression for
locally advanced prostate cancer? Data from the TROG 03.04 RADAR trial.
\emph{Radiotherapy and Oncology}, \emph{115}(3), 301--307.
\url{https://doi.org/10.1016/j.radonc.2015.05.016}}

\leavevmode\hypertarget{ref-grady_gp_2015}{}%
\CSLLeftMargin{209. }
\CSLRightInline{Grady, A., Carey, M., Oldmeadow, C., Bryant, J., Mazza,
D., \& Sanson-Fisher, R. (2015). GP detection of health risk factors
among general practice patients at risk of primary and secondary stroke.
\emph{Family Practice}, \emph{32}(3), 336--342.
\url{https://doi.org/10.1093/fampra/cmv024}}

\leavevmode\hypertarget{ref-kelly_study_2015}{}%
\CSLLeftMargin{210. }
\CSLRightInline{Kelly, P. J., Baker, A. L., Deane, F. P., Callister, R.,
Collins, C. E., Oldmeadow, C., Attia, J. R., Townsend, C. J., Ingram,
I., Byrne, G., \& Keane, C. A. (2015). Study protocol: A stepped wedge
cluster randomised controlled trial of a healthy lifestyle intervention
for people attending residential substance abuse treatment. \emph{BMC
Public Health}, \emph{15}, 465--465.
\url{https://doi.org/10.1186/s12889-015-1729-y}}

\leavevmode\hypertarget{ref-khan_effect_2020}{}%
\CSLLeftMargin{211. }
\CSLRightInline{Khan, M. N., Harris, M. L., Oldmeadow, C., \& Loxton, D.
(2020). Effect of unintended pregnancy on skilled antenatal care uptake
in Bangladesh: Analysis of national survey data. \emph{Archives of
Public Health = Archives Belges De Sante Publique}, \emph{78}, 81.
\url{https://doi.org/10.1186/s13690-020-00468-1}}

\leavevmode\hypertarget{ref-magin_gp_2015}{}%
\CSLLeftMargin{212. }
\CSLRightInline{Magin, P., Morgan, S., Wearne, S., Tapley, A.,
Henderson, K., Oldmeadow, C., Ball, J., Scott, J., Spike, N., McArthur,
L., \& Driel, M. van. (2015). GP trainees' in-consultation
information-seeking: Associations with human, paper and electronic
sources. \emph{Family Practice}, \emph{32}(5), 525--532.
\url{https://doi.org/10.1093/fampra/cmv047}}

\leavevmode\hypertarget{ref-holliday_pattern_2015}{}%
\CSLLeftMargin{213. }
\CSLRightInline{Holliday, S., Morgan, S., Tapley, A., Dunlop, A.,
Henderson, K., Driel, M. van, Spike, N., Mcarthur, L., Ball, J.,
Oldmeadow, C., \& Magin, P. (2015). The Pattern of Opioid Management by
Australian General Practice Trainees. \emph{Pain Medicine (United
States)}, \emph{16}(9), 1720--1731.
\url{https://doi.org/10.1111/pme.12820}}

\leavevmode\hypertarget{ref-noble_which_2015}{}%
\CSLLeftMargin{214. }
\CSLRightInline{Noble, N., Paul, C., Turon, H., \& Oldmeadow, C. (2015).
Which modifiable health risk behaviours are related? A systematic review
of the clustering of Smoking, Nutrition, Alcohol and Physical activity
('SNAP') health risk factors. \emph{Preventive Medicine}, \emph{81},
16--41. \url{https://doi.org/10.1016/j.ypmed.2015.07.003}}

\leavevmode\hypertarget{ref-rifat_factors_2015}{}%
\CSLLeftMargin{215. }
\CSLRightInline{Rifat, M., Hall, J., Oldmeadow, C., Husain, A.,
Hinderaker, S. G., \& Milton, A. H. (2015). Factors related to previous
tuberculosis treatment of patients with multidrugresistant tuberculosis
in Bangladesh. \emph{BMJ Open}, \emph{5}(9).
\url{https://doi.org/10.1136/bmjopen-2015-008273}}

\leavevmode\hypertarget{ref-kay-lambkin_itread_2015}{}%
\CSLLeftMargin{216. }
\CSLRightInline{Kay-Lambkin, F. J., Baker, A. L., Geddes, J., Hunt, S.
A., Woodcock, K. L., Teesson, M., Oldmeadow, C., Lewin, T. J., Bewick,
B. M., Brady, K., Spring, B., Deady, M., Barrett, E., \& Thornton, L.
(2015). The iTreAD project: A study protocol for a randomised controlled
clinical trial of online treatment and social networking for binge
drinking and depression in young people Health behavior, health
promotion and society. \emph{BMC Public Health}, \emph{15}(1).
\url{https://doi.org/10.1186/s12889-015-2365-2}}

\leavevmode\hypertarget{ref-morgan_pathology_2015}{}%
\CSLLeftMargin{217. }
\CSLRightInline{Morgan, S., Henderson, K. M., Tapley, A., Scott, J., Van
Driel, M. L., Spike, N. A., Mcarthur, L. A., Davey, A. R., Oldmeadow,
C., Ball, J., \& Magin, P. J. (2015). Pathology test-ordering behaviour
of Australian general practice trainees: A cross-sectional analysis.
\emph{International Journal for Quality in Health Care}, \emph{27}(6),
528--535. \url{https://doi.org/10.1093/intqhc/mzv086}}

\leavevmode\hypertarget{ref-yoong_alignment_2015}{}%
\CSLLeftMargin{218. }
\CSLRightInline{Yoong, S. L., Hall, A., Williams, C. M., Skelton, E.,
Oldmeadow, C., Wiggers, J., Karimkhani, C., Boyers, L. N., Dellavalle,
R. P., Hilton, J., \& Wolfenden, L. (2015). Alignment of systematic
reviews published in the Cochrane database of systematic reviews and the
database of abstracts and reviews of effectiveness with global
burden-of-disease data: A bibliographic analysis. \emph{Journal of
Epidemiology and Community Health}, \emph{69}(7), 708--714.
\url{https://doi.org/10.1136/jech-2014-205389}}

\leavevmode\hypertarget{ref-iseme_autoantibodies_2015}{}%
\CSLLeftMargin{219. }
\CSLRightInline{Iseme, R. A., McEvoy, M., Kelly, B., Agnew, L., Attia,
J., Walker, F. R., Oldmeadow, C., \& Boyle, M. (2015). Autoantibodies
are not predictive markers for the development of depressive symptoms in
a population-based cohort of older adults. \emph{European Psychiatry},
\emph{30}(6), 694--700.
\url{https://doi.org/10.1016/j.eurpsy.2015.06.006}}

\leavevmode\hypertarget{ref-chan_genetics_2015}{}%
\CSLLeftMargin{220. }
\CSLRightInline{Chan, J. P. L., Thalamuthu, A., Oldmeadow, C.,
Armstrong, N. J., Holliday, E. G., McEvoy, M., Kwok, J. B., Assareh, A.
A., Peel, R., Hancock, S. J., Reppermund, S., Menant, J., Trollor, J.
N., Brodaty, H., Schofield, P. R., Attia, J. R., Sachdev, P. S., Scott,
R. J., \& Mather, K. A. (2015). Genetics of hand grip strength in mid to
late life. \emph{Age}, \emph{37}(1), 1--10.
\url{https://doi.org/10.1007/s11357-015-9745-5}}

\leavevmode\hypertarget{ref-griffin_receptor_2020}{}%
\CSLLeftMargin{221. }
\CSLRightInline{Griffin, N., Marsland, M., Roselli, S., Oldmeadow, C.,
Attia, J., Walker, M. M., Hondermarck, H., \& Faulkner, S. (2020). The
Receptor Tyrosine Kinase TrkA Is Increased and Targetable in
HER2-Positive Breast Cancer. \emph{Biomolecules}, \emph{10}(9).
\url{https://doi.org/10.3390/biom10091329}}

\leavevmode\hypertarget{ref-rifat_health_2015}{}%
\CSLLeftMargin{222. }
\CSLRightInline{Rifat, M., Hall, J., Milton, A. H., Oldmeadow, C., \&
Husain, A. (2015). Health system delay in treatment of multidrug
resistant tuberculosis patients in Bangladesh. \emph{BMC Infectious
Diseases}, \emph{2015}(526), 1--8.
\url{https://doi.org/10.1186/s12879-015-1253-9}}

\leavevmode\hypertarget{ref-abdullah_characterizing_2015}{}%
\CSLLeftMargin{223. }
\CSLRightInline{Abdullah, N., Abdul Murad, N. A., Attia, J., Oldmeadow,
C., Mohd Haniff, E. A., Syafruddin, S. E., Abd Jalal, N., Ismail, N.,
Ishak, M., Jamal, R., Scott, R. J., \& Holliday, E. G. (2015).
Characterizing the genetic risk for Type 2 diabetes in a Malaysian
multi-ethnic cohort. \emph{Diabetic Medicine}, \emph{32}(10),
1377--1384. \url{https://doi.org/10.1111/dme.12735}}

\leavevmode\hypertarget{ref-kable_nurse_2015}{}%
\CSLLeftMargin{224. }
\CSLRightInline{Kable, A., James, C., Snodgrass, S., Plotnikoff, R.,
Guest, M., Ashby, S., Oldmeadow, C., \& Collins, C. (2015). Nurse
provision of healthy lifestyle advice to people who are overweight or
obese. \emph{Nursing and Health Sciences}, \emph{17}(4), 451--459.}

\leavevmode\hypertarget{ref-thomson_clinical_2016}{}%
\CSLLeftMargin{225. }
\CSLRightInline{Thomson, A., Morgan, S., O'Mara, P., Tapley, A.,
Henderson, K., Van Driel, M., Oldmeadow, C., Ball, J., Scott, J., Spike,
N., McArthur, L., \& Magin, P. (2016). Clinical encounters of Australian
general practice registrars with Aboriginal and Torres Strait Islander
patients. \emph{Australian and New Zealand Journal of Public Health},
\emph{40}, S75--S80. \url{https://doi.org/10.1111/1753-6405.12412}}

\leavevmode\hypertarget{ref-mather_genome-wide_2016}{}%
\CSLLeftMargin{226. }
\CSLRightInline{Mather, K. A., Thalamuthu, A., Oldmeadow, C., Song, F.,
Armstrong, N. J., Poljak, A., Holliday, E. G., McEvoy, M., Kwok, J. B.,
Assareh, A. A., Reppermund, S., Kochan, N. A., Lee, T., Ames, D.,
Wright, M. J., Trollor, J. N., Schofield, P. W., Brodaty, H., Scott, R.
J., \ldots{} Sachdev, P. S. (2016). Genome-wide significant results
identified for plasma apolipoprotein H levels in middle-aged and older
adults. \emph{Scientific Reports}, \emph{6}.
\url{https://doi.org/10.1038/srep23675}}

\leavevmode\hypertarget{ref-ashman_maternal_2016}{}%
\CSLLeftMargin{227. }
\CSLRightInline{Ashman, A. M., Collins, C. E., Hure, A. J., Jensen, M.,
\& Oldmeadow, C. (2016). Maternal diet during early childhood, but not
pregnancy, predicts diet quality and fruit and vegetable acceptance in
offspring. \emph{Maternal and Child Nutrition}, \emph{12}(3), 579--590.
\url{https://doi.org/10.1111/mcn.12151}}

\leavevmode\hypertarget{ref-ibrahim-verbaas_gwas_2016}{}%
\CSLLeftMargin{228. }
\CSLRightInline{Ibrahim-Verbaas, C. A., Bressler, J., Debette, S.,
Schuur, M., Smith, A. V., Bis, J. C., Davies, G., Trompet, S., Smith, J.
A., Wolf, C., Chibnik, L. B., Liu, Y., Vitart, V., Kirin, M., Petrovic,
K., Polasek, O., Zgaga, L., Fawns-Ritchie, C., Hoffmann, P., \ldots{}
Chasman, D. I. (2016). GWAS for executive function and processing speed
suggests involvement of the CADM2 gene. \emph{Molecular Psychiatry},
\emph{21}(2), 189--197. \url{https://doi.org/10.1038/mp.2015.37}}

\leavevmode\hypertarget{ref-turnock_prevalence_2016}{}%
\CSLLeftMargin{229. }
\CSLRightInline{Turnock, A., Morgan, S., Henderson, K., Tapley, A., Van
Driel, M., Oldmeadow, C., Ball, J., Presser, J., Davey, A., Scott, J.,
\& Magin, P. (2016). Prevalence and associations of general practice
nurses' involvement in consultations of general practitioner registrars:
A cross-sectional analysis. \emph{Australian Health Review},
\emph{40}(1), 92--99. \url{https://doi.org/10.1071/AH15010}}

\leavevmode\hypertarget{ref-kay-lambkin_study_2016}{}%
\CSLLeftMargin{230. }
\CSLRightInline{Kay-Lambkin, F. J., Thornton, L., Lappin, J. M.,
Hanstock, T., Sylvia, L., Jacka, F., Baker, A. L., Berk, M., Mitchell,
P. B., Callister, R., Rogers, N., Webster, S., Dennis, S., Oldmeadow,
C., MacKinnon, A., Doran, C., Turner, A., \& Hunt, S. (2016). Study
protocol for a systematic review of evidence for lifestyle interventions
targeting smoking, sleep, alcohol/other drug use, physical activity, and
healthy diet in people with bipolar disorder. \emph{Systematic Reviews},
\emph{5}(1). \url{https://doi.org/10.1186/s13643-016-0282-9}}

\leavevmode\hypertarget{ref-thomson_recording_2016}{}%
\CSLLeftMargin{231. }
\CSLRightInline{Thomson, A., Morgan, S., O'Mara, P., Tapley, A.,
Henderson, K., Van Driel, M., Oldmeadow, C., Ball, J., Scott, J., Spike,
N., McArthur, L., \& Magin, P. (2016). The recording of Aboriginal and
Torres Strait Islander status in general practice clinical records: A
cross-sectional study. \emph{Australian and New Zealand Journal of
Public Health}, \emph{40}, S70--S74.
\url{https://doi.org/10.1111/1753-6405.12400}}

\leavevmode\hypertarget{ref-guillaumier_self-exempting_2016}{}%
\CSLLeftMargin{232. }
\CSLRightInline{Guillaumier, A., Bonevski, B., Paul, C., D este, C.,
Twyman, L., Palazzi, K., \& Oldmeadow, C. (2016). Self-exempting beliefs
and intention to quit smoking within a socially disadvantaged Australian
sample of smokers. \emph{International Journal of Environmental Research
and Public Health}, \emph{13}(1).
\url{https://doi.org/10.3390/ijerph13010118}}

\leavevmode\hypertarget{ref-minelli_association_2016}{}%
\CSLLeftMargin{233. }
\CSLRightInline{Minelli, C., Dean, C. H., Hind, M., Alves, A. C.,
Amaral, A. F. S., Siroux, V., Huikari, V., Artigas, M. S., Evans, D. M.,
Loth, D. W., Bossé, Y., Postma, D. S., Sin, D., Thompson, J., Demenais,
F., Henderson, J., Bouzigon, E., Jarvis, D., Järvelin, M. R., \ldots{}
Garcia, M. (2016). Association of Forced Vital Capacity with the
Developmental Gene NCOR2. \emph{PLoS ONE}, \emph{11}(2).
\url{https://doi.org/10.1371/journal.pone.0147388}}

\leavevmode\hypertarget{ref-dallas_antibiotic_2016}{}%
\CSLLeftMargin{234. }
\CSLRightInline{Dallas, A., Driel, M. van, Morgan, S., Tapley, A.,
Henderson, K., Ball, J., Oldmeadow, C., Davey, A., Mulquiney, K., Davis,
J., Spike, N., McArthur, L., \& Magin, P. (2016). Antibiotic prescribing
for sore throat: A cross-sectional analysis of the ReCEnT study
exploring the habits of early-career doctors in family practice.
\emph{Family Practice}, \emph{33}(3), 302--308.
\url{https://doi.org/10.1093/fampra/cmw014}}

\leavevmode\hypertarget{ref-anne_immersion_2016}{}%
\CSLLeftMargin{235. }
\CSLRightInline{Anne, S., Tse, R., Oldmeadow, C., Attia, J. R., \& Cala,
A. D. (2016). Immersion of bovine eyeballs after 1 hour in seawater does
not result in elevation of postmortem vitreous humor sodium and chloride
levels. \emph{American Journal of Forensic Medicine and Pathology},
\emph{37}(2), 108--111.
\url{https://doi.org/10.1097/PAF.0000000000000229}}

\leavevmode\hypertarget{ref-fradgley_cross-sectional_2016}{}%
\CSLLeftMargin{236. }
\CSLRightInline{Fradgley, E. A., Bryant, J., Paul, C. L., Hall, A. E.,
Sanson-Fisher, R. W., \& Oldmeadow, C. (2016). Cross-sectional data that
explore the relationship between outpatients' quality of life and
preferences for quality improvement in oncology settings. \emph{Journal
of Oncology Practice}, \emph{12}(6), e746--e754.
\url{https://doi.org/10.1200/JOP.2016.011023}}

\leavevmode\hypertarget{ref-okbay_genetic_2016}{}%
\CSLLeftMargin{237. }
\CSLRightInline{Okbay, A., Baselmans, B. M. L., De Neve, J. E., Turley,
P., Nivard, M. G., Fontana, M. A., Meddens, S. F. W., Linnér, R. K.,
Rietveld, C. A., Derringer, J., Gratten, J., Lee, J. J., Liu, J. Z., De
Vlaming, R., SAhluwalia, T., Buchwald, J., Cavadino, A., Frazier-Wood,
A. C., Furlotte, N. A., \ldots{} Trzaskowski, M. (2016). Genetic
variants associated with subjective well-being, depressive symptoms, and
neuroticism identified through genome-wide analyses. \emph{Nature
Genetics}, \emph{48}(6), 624--633.
\url{https://doi.org/10.1038/ng.3552}}

\leavevmode\hypertarget{ref-okbay_genome-wide_2016}{}%
\CSLLeftMargin{238. }
\CSLRightInline{Okbay, A., Beauchamp, J. P., Fontana, M. A., Lee, J. J.,
Pers, T. H., Rietveld, C. A., Turley, P., Chen, G. B., Emilsson, V.,
Meddens, S. F. W., Oskarsson, S., Pickrell, J. K., Thom, K., Timshel,
P., De Vlaming, R., Abdellaoui, A., Ahluwalia, T. S., Bacelis, J.,
Baumbach, C., \ldots{} Horan, M. A. (2016). Genome-wide association
study identifies 74 loci associated with educational attainment.
\emph{Nature}, \emph{533}(7604), 539--542.
\url{https://doi.org/10.1038/nature17671}}

\leavevmode\hypertarget{ref-mandaliya_psychosocial_2016}{}%
\CSLLeftMargin{239. }
\CSLRightInline{Mandaliya, H., Ansari, Z., Evans, T., Oldmeadow, C., \&
George, M. (2016). Psychosocial analysis of cancer survivors in rural
Australia: Focus on demographics, quality of life and financial domains.
\emph{Asian Pacific Journal of Cancer Prevention}, \emph{17}(5),
2459--2464. \url{https://doi.org/10.7314/APJCP.2016.17.5.2459}}

\leavevmode\hypertarget{ref-garland_elevation_2016}{}%
\CSLLeftMargin{240. }
\CSLRightInline{Garland, J., Tse, R., Oldmeadow, C., Attia, J., Anne,
S., \& Cala, A. D. (2016). Elevation of post mortem vitreous humour
sodium and chloride levels can be used as a reliable test in cases of
suspected salt water drowning when the immersion times are less than one
hour. \emph{Forensic Science International}, \emph{266}, 338--342.
\url{https://doi.org/10.1016/j.forsciint.2016.06.001}}

\leavevmode\hypertarget{ref-bryant_consumer_2016}{}%
\CSLLeftMargin{241. }
\CSLRightInline{Bryant, J., Sanson-Fisher, R., Fradgley, E., Hobden, B.,
Zucca, A., Henskens, F., Searles, A., Webb, B., \& Oldmeadow, C. (2016).
A consumer register: An acceptable and cost-effective alternative for
accessing patient populations. \emph{BMC Medical Research Methodology},
\emph{16}(1), 134.}

\leavevmode\hypertarget{ref-fealy_demographic_2020}{}%
\CSLLeftMargin{242. }
\CSLRightInline{Fealy, S., Attia, J., Leigh, L., Oldmeadow, C.,
Hazelton, M., Foureur, M., Collins, C. E., Smith, R., \& Hure, A.
(2020). Demographic and social-cognitive factors associated with
gestational weight gain in an Australian pregnancy cohort. \emph{Eating
Behaviors}, \emph{39}, 101430.
\url{https://doi.org/10.1016/j.eatbeh.2020.101430}}

\leavevmode\hypertarget{ref-marioni_genetic_2016}{}%
\CSLLeftMargin{243. }
\CSLRightInline{Marioni, R. E., Ritchie, S. J., Joshi, P. K., Hagenaars,
S. P., Okbay, A., Fischer, K., Adams, M. J., Hill, W. D., Davies, G.,
Nagy, R., Amador, C., Läll, K., Metspalu, A., Liewald, D. C., Campbell,
A., Wilson, J. F., Hayward, C., Esko, T., Porteous, D. J., \ldots{}
Cappuccio, F. P. (2016). Genetic variants linked to education predict
longevity. \emph{Proceedings of the National Academy of Sciences of the
United States of America}, \emph{113}(47), 13366--13371.
\url{https://doi.org/10.1073/pnas.1605334113}}

\leavevmode\hypertarget{ref-twyman_association_2016}{}%
\CSLLeftMargin{244. }
\CSLRightInline{Twyman, L., Bonevski, B., Paul, C., Kay-Lambkin, F. J.,
Bryant, J., Oldmeadow, C., Palazzi, K., \& Guillaumier, A. (2016). The
association between cannabis use and motivation and intentions to quit
tobacco within a sample of Australian socioeconomically disadvantaged
smokers. \emph{Health Education Research}, \emph{31}(6), 771--781.
\url{https://doi.org/10.1093/her/cyw049}}

\leavevmode\hypertarget{ref-anderson_evaluation_2016}{}%
\CSLLeftMargin{245. }
\CSLRightInline{Anderson, D., Phelan, H., Jones, K., Smart, C.,
Oldmeadow, C., King, B., \& Crock, P. (2016). Evaluation of a novel
continuous glucose monitoring guided system for adjustment of insulin
dosing~--~PumpTune: A randomized controlled trial. \emph{Pediatric
Diabetes}, \emph{17}(7), 478--482.
\url{https://doi.org/10.1111/pedi.12332}}

\leavevmode\hypertarget{ref-fradgley_getting_2016}{}%
\CSLLeftMargin{246. }
\CSLRightInline{Fradgley, E. A., Paul, C. L., Bryant, J., \& Oldmeadow,
C. (2016). Getting right to the point: Identifying Australian
outpatients' priorities and preferences for patient-centred quality
improvement in chronic disease care. \emph{International Journal for
Quality in Health Care}, \emph{28}(4), 470--477.
\url{https://doi.org/10.1093/intqhc/mzw049}}

\leavevmode\hypertarget{ref-gunathilake_association_2016}{}%
\CSLLeftMargin{247. }
\CSLRightInline{Gunathilake, R., Oldmeadow, C., McEvoy, M., Inder, K.
J., Schofield, P. W., Nair, B. R., \& Attia, J. (2016). The association
between obesity and cognitive function in older persons: How much is
mediated by inflammation, fasting plasma glucose, and
hypertriglyceridemia? \emph{Journals of Gerontology - Series A
Biological Sciences and Medical Sciences}, \emph{71}(12), 1603--1608.
\url{https://doi.org/10.1093/gerona/glw070}}

\leavevmode\hypertarget{ref-de_vries_comparison_2017}{}%
\CSLLeftMargin{248. }
\CSLRightInline{De Vries, P. S., Sabater-Lleal, M., Chasman, D. I.,
Trompet, S., Ahluwalia, T. S., Teumer, A., Kleber, M. E., Chen, M. H.,
Wang, J. J., Attia, J. R., Marioni, R. E., Steri, M., Weng, L. C., Pool,
R., Grossmann, V., Brody, J. A., Venturini, C., Tanaka, T., Rose, L. M.,
\ldots{} Dehghan, A. (2017). Comparison of HapMap and 1000 genomes
reference panels in a large-scale genome-wide association study.
\emph{PLoS ONE}, \emph{12}(1).
\url{https://doi.org/10.1371/journal.pone.0167742}}

\leavevmode\hypertarget{ref-zhang_increasing_2017}{}%
\CSLLeftMargin{249. }
\CSLRightInline{Zhang, X., Khan, A. A., Haq, E. U., Rahim, A., Hu, D.,
Attia, J., Oldmeadow, C., Ma, X., Ding, R., \& Boyle, A. J. (2017).
Increasing mortality from ischaemic heart disease in China from 2004 to
2010: Disproportionate rise in rural areas and elderly subjects. 438
million person-years follow-up. \emph{European Heart Journal - Quality
of Care and Clinical Outcomes}, \emph{3}(1), 47--52.
\url{https://doi.org/10.1093/ehjqcco/qcw041}}

\leavevmode\hypertarget{ref-bar_zeev_opportunities_2016}{}%
\CSLLeftMargin{250. }
\CSLRightInline{Bar Zeev, Y., Bonevski, B., Tywman, L., Watt, K.,
Clarke, M., Atkins, L., Palazzi, K., Oldmeadow, C., \& Gould, G. S.
(2016). Opportunities missed: A cross-sectional survey of the provision
of smoking cessation care to pregnant women by Australian General
Practitioners and Obstetricians. \emph{Nicotine and Tobacco Research},
636--641. \url{https://doi.org/10.1093/ntr/ntw331}}

\leavevmode\hypertarget{ref-waller_perceptions_2020}{}%
\CSLLeftMargin{251. }
\CSLRightInline{Waller, A., Chan, S., Chan, C. W. H., Chow, M. C. M.,
Kim, M., Kang, S. J., Oldmeadow, C., \& Sanson-Fisher, R. (2020).
Perceptions of optimal end-of-life care in hospitals: A cross-sectional
study of nurses in three locations. \emph{Journal of Advanced Nursing}.
\url{https://doi.org/10.1111/jan.14510}}

\leavevmode\hypertarget{ref-clover_reduced_2017}{}%
\CSLLeftMargin{252. }
\CSLRightInline{Clover, K. A., Rogers, K. M., Britton, B., Oldmeadow,
C., Attia, J., \& Carter, G. L. (2017). Reduced prevalence of pain and
distress during 4 years of screening with QUICATOUCH in Australian
oncology patients. \emph{European Journal of Cancer Care}, \emph{26}(6),
1--10. \url{https://doi.org/10.1111/ecc.12636}}

\leavevmode\hypertarget{ref-laver_cardiac_2017}{}%
\CSLLeftMargin{253. }
\CSLRightInline{Laver, D. R., Attia, J., Oldmeadow, C., \& Quail, A. W.
(2017). Cardiac Calcium Release Channel (Ryanodine Receptor 2)
Regulation by Halogenated Anesthetics. \emph{Anesthesiology},
\emph{126}(3), 495--506.
\url{https://doi.org/10.1097/ALN.0000000000001519}}

\leavevmode\hypertarget{ref-dallas_antibiotic_2017}{}%
\CSLLeftMargin{254. }
\CSLRightInline{Dallas, A., Driel, M. van, Morgan, S., Tapley, A.,
Henderson, K., Oldmeadow, C., Ball, J., Davey, A., Mulquiney, K., Davis,
J., Spike, N., McArthur, L., Stewart, R., \& Magin, P. (2017).
Antibiotic prescribing for acute otitis media and acute sinusitis: A
cross-sectional analysis of the ReCEnT study exploring the habits of
early career doctors in family practice. \emph{Family Practice},
\emph{34}(2), 180--187. \url{https://doi.org/10.1093/fampra/cmw144}}

\leavevmode\hypertarget{ref-gleeson_developing_2017}{}%
\CSLLeftMargin{255. }
\CSLRightInline{Gleeson, M., Pyne, D. B., Elkington, L. J., Hall, S. T.,
Attia, J. R., Oldmeadow, C., Wood, L. G., \& Callister, R. (2017).
Developing a multi-component immune model for evalusating the risk of
respiratory illness in athletes. \emph{EXERCISE IMMUNOLOGY REVIEW},
\emph{23}, 52--64.}

\leavevmode\hypertarget{ref-davies_disparities_2017}{}%
\CSLLeftMargin{256. }
\CSLRightInline{Davies, A. J., Naudin, C., Al-Omary, M., Khan, A.,
Oldmeadow, C., Jones, M., Bastian, B., Bhagwandeen, R., Fletcher, P.,
Leitch, J., \& Boyle, A. (2017). Disparities in the incidence of acute
myocardial infarction: Long-term trends from the Hunter region.
\emph{Internal Medicine Journal}, \emph{47}(5), 557--562.
\url{https://doi.org/10.1111/imj.13399}}

\leavevmode\hypertarget{ref-joshi_duration_2017}{}%
\CSLLeftMargin{257. }
\CSLRightInline{Joshi, T., Oldmeadow, C., Attia, J., \& Wynne, K.
(2017). The duration of intrapartum maternal hyperglycaemia predicts
neonatal hypoglycaemia in women with pre-existing diabetes.
\emph{Diabetic Medicine}, \emph{34}(5), 725--731.
\url{https://doi.org/10.1111/dme.13337}}

\leavevmode\hypertarget{ref-harris_stress_2017}{}%
\CSLLeftMargin{258. }
\CSLRightInline{Harris, M. L., Oldmeadow, C., Hure, A., Luu, J., Loxton,
D., \& Attia, J. (2017). Stress increases the risk of type 2 diabetes
onset in women: A 12-year longitudinal study using causal modelling.
\emph{PLOS ONE}, \emph{12}(2).
\url{https://doi.org/10.1371/journal.pone.0172126}}

\leavevmode\hypertarget{ref-warren_genome-wide_2017-1}{}%
\CSLLeftMargin{259. }
\CSLRightInline{Warren, H. R., Evangelou, E., Cabrera, C. P., Gao, H.,
Ren, M., Mifsud, B., Ntalla, I., Surendran, P., Liu, C., Cook, J. P.,
Kraja, A. T., Drenos, F., Loh, M., Verweij, N., Marten, J., Karaman, I.,
Segura Lepe, M. P., O'Reilly, P. F., Knight, J., \ldots{} Luan, J.
(2017). Genome-wide association analysis identifies novel blood pressure
loci and offers biological insights into cardiovascular risk.
\emph{Nature Genetics}, \emph{49}(3), 403--415.
\url{https://doi.org/10.1038/ng.3768}}

\leavevmode\hypertarget{ref-dodd_testing_2017}{}%
\CSLLeftMargin{260. }
\CSLRightInline{Dodd, N., Carey, M. L., Mansfield, E., \& Oldmeadow, C.
(2017). Testing the Effectiveness of a Primary Care Intervention to
Improve Uptake of Colorectal Cancer Screening: A Randomized Controlled
Trial Protocol. \emph{JMIR RESEARCH PROTOCOLS}, \emph{6}(5).
\url{https://doi.org/10.2196/resprot.7432}}

\leavevmode\hypertarget{ref-abdullah_predicting_2017}{}%
\CSLLeftMargin{261. }
\CSLRightInline{Abdullah, N., Abdul Murad, N. A., Mohd Haniff, E. A.,
Syafruddin, S. E., Attia, J., Oldmeadow, C., Kamaruddin, M. A., Abd
Jalal, N., Ismail, N., Ishak, M., Jamal, R., Scott, R. J., \& Holliday,
E. G. (2017). Predicting type 2 diabetes using genetic and environmental
risk factors in a multi-ethnic Malaysian cohort. \emph{Public Health},
\emph{149}, 31--38. \url{https://doi.org/10.1016/j.puhe.2017.04.003}}

\leavevmode\hypertarget{ref-zdenkowski_treatment_2017}{}%
\CSLLeftMargin{262. }
\CSLRightInline{Zdenkowski, N., Radvan, G., Pugliese, L., Charlton, J.,
Oldmeadow, C., Fraser, A., \& Bonaventura, A. (2017). Treatment of
pancreatic insufficiency using pancreatic extract in patients with
advanced pancreatic cancer: A pilot study (PICNIC). \emph{Supportive
Care in Cancer}, \emph{25}(6), 1963--1971.
\url{https://doi.org/10.1007/s00520-017-3602-2}}

\leavevmode\hypertarget{ref-gould_exploring_2017}{}%
\CSLLeftMargin{263. }
\CSLRightInline{Gould, G. S., Bovill, M., Chiu, S., Bonevski, B., \&
Oldmeadow, C. (2017). Exploring an adapted Risk Behaviour Diagnosis
Scale among Indigenous Australian women who had experiences of smoking
during pregnancy: A cross-sectional survey in regional New South Wales,
Australia. \emph{BMJ Open}, \emph{7}(5).
\url{https://doi.org/10.1136/bmjopen-2016-015054}}

\leavevmode\hypertarget{ref-willems_large-scale_2017}{}%
\CSLLeftMargin{264. }
\CSLRightInline{Willems, S. M., Wright, D. J., Day, F. R., Trajanoska,
K., Joshi, P. K., Morris, J. A., Matteini, A. M., Garton, F. C., Grarup,
N., Oskolkov, N., Thalamuthu, A., Mangino, M., Liu, J., Demirkan, A.,
Lek, M., Xu, L., Wang, G., Oldmeadow, C., Gaulton, K. J., \ldots{}
Kammerer, C. (2017). Large-scale GWAS identifies multiple loci for hand
grip strength providing biological insights into muscular fitness.
\emph{Nature Communications}, \emph{8}.
\url{https://doi.org/10.1038/ncomms16015}}

\leavevmode\hypertarget{ref-wain_novel_2017}{}%
\CSLLeftMargin{265. }
\CSLRightInline{Wain, L. V., Vaez, A., Jansen, R., Joehanes, R., Van Der
Most, P. J., Erzurumluoglu, A. M., O'Reilly, P. F., Cabrera, C. P.,
Warren, H. R., Rose, L. M., Verwoert, G. C., Hottenga, J. J.,
Strawbridge, R. J., Esko, T., Arking, D. E., Hwang, S. J., Guo, X.,
Kutalik, Z., Trompet, S., \ldots{} Harris, T. B. (2017). Novel Blood
Pressure Locus and Gene Discovery Using Genome-Wide Association Study
and Expression Data Sets from Blood and the Kidney. \emph{Hypertension},
\emph{70}(3), e4--e19.
\url{https://doi.org/10.1161/HYPERTENSIONAHA.117.09438}}

\leavevmode\hypertarget{ref-dodd_are_2017}{}%
\CSLLeftMargin{266. }
\CSLRightInline{Dodd, N., Mansfield, E., Carey, M., \& Oldmeadow, C.
(2017). Are Australian general practice patients appropriately screened
for colorectal cancer? A cross-sectional study. \emph{Australasian
Medical Journal}, \emph{10}(7), 610--619.
\url{https://doi.org/10.21767/AMJ.2017.3041}}

\leavevmode\hypertarget{ref-blyton_pilot_2020}{}%
\CSLLeftMargin{267. }
\CSLRightInline{Blyton, S. J., Edwards, S., Moghaddas, D., Zoete, R. M.
J. de, Palazzi, K., Oldmeadow, C., Bolton, P., Rivett, D. A., \&
Snodgrass, S. J. (2020). A Pilot Longitudinal Study of 3-Dimensional
Head and Neck Kinematics During Functional Tasks in Individuals With
Chronic Idiopathic Neck Pain Either Wait-Listed for or Receiving
Chiropractic Spinal Manipulative Therapy With Exercise. \emph{Journal of
Manipulative and Physiological Therapeutics}.
\url{https://doi.org/10.1016/j.jmpt.2019.01.003}}

\end{document}
